---
title: "Classification Tree"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Using the package "Tree"

```{r , echo=TRUE}
library(tree)

```

Predicting whether the organization's purpose is religious

```{r , echo=FALSE}
library(tree)
dat <- read.csv("~/Dropbox (ASU)/USC Mission Paper/Data and Analysis/github_files/machine_learning_mission_codes/DATA/Name Mission Program w Corpus and DFM.csv")
dat2 <- (dat[,120:ncol(dat)])

others <- dat[,c("Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposereligious")]
dat2 <- cbind(dat2, others)
dat2 <- subset(dat2, select=-document)

dat2$list <- 1:nrow(dat2)

```

Data needs to be factor to classify, so I restructure the outcome variable. Set up seperate data frame with the training data.

```{r, echo=T}

set.seed(500)
train <- sample(1:nrow(dat2), 1200)

dat2$religiousorg <- ifelse(dat2$Orgpurposereligious==1, "religious", "none")
dat2$religiousorg <- as.factor(dat2$religiousorg)

train.dat <- dat2[(dat2$list %in% train), ]


```

-Orgpurposereligious prevents use of the outcome variable in a different form for prediction. We can see the tree that is formed with labels.
```{r, echo=T}
tree.religion = tree(religiousorg~.-Orgpurposereligious, data=train.dat)


plot(tree.religion)
text(tree.religion, pretty=0, cex=.5)
```
```{r, echo=F}

```
How well does it classify? We can see how the test data does with the training model.


```{r, echo=T}

tree.pred = predict(tree.religion, dat2[-train,], type="class")
with(dat2[-train,], table(tree.pred, religiousorg))
```

