---
title: "Classifying Org Purpose with Naive Bayes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
library(e1071)
library(caret) #confusion matrix
library(quanteda) # naive bayes
library(pander) #attractive tables in rmarkdown
```

Calling in data from github. The second step removes all of the columns that preceed the document-features matrix that we don't want to include

```{r, echo=TRUE}
dat <- read.csv( "~/Dropbox (ASU)/USC Mission Paper/Data and Analysis/github_files/machine_learning_mission_codes/DATA/Name Mission Program w Corpus and DFM.csv" )
dat2 <- (dat[,119:ncol(dat)])


```

Selecting one purpose varaible as the outcome we classify and then adding it backto the DFM. Could also add additional variables of interest at this stage

```{r , echo=TRUE}
others <- dat[,c("Incorporatedstate","Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposecharitable")]
dat2 <- cbind(dat2, others)

```

Selecting a subset of observations as a training set

```{r, echo=TRUE}

set.seed(300)
id_train <- sample(1:nrow(dat2), 1000, replace = FALSE)
head(id_train, 10)
```

Changing out data to a corpus as an intermediatry step to convert it to a dfm

```{r , echo=TRUE}

dat2$id_numeric <- 1:nrow(dat2)
dat.corpus <- data.frame(lapply(dat2, as.character), stringsAsFactors=FALSE)
dat.corpus <- corpus(dat.corpus,        text_field = "Corpus")


```
With a corpus, we can use corpus_subset in order to selct the observations that are and are not in the trainging set. The final bit of code then converts it to a dfm. The naive bayes command requires a dfm

```{r, echo=TRUE}
training_nb <- corpus_subset(dat.corpus, id_numeric %in% id_train)%>%
    dfm(stem = TRUE)

test_nb <- corpus_subset(dat.corpus, !id_numeric %in% id_train)%>%
    dfm(stem = TRUE)

```

textmodel_nb runs the naive bayes for the training set

```{r, echo=TRUE}

train_results <- textmodel_nb(training_nb, docvars(training_nb, "Orgpurposecharitable"))
summary(train_results)
```

need to make sure features in the two data sets match before using the training data on the test set

```{r, echo=TRUE}
dfmat_matched <- dfm_select(test_nb, pattern=training_nb, selection = "keep")


```

Here we use the training data with the test data and see how well it performed

```{r, echo=TRUE}
actual_class <- docvars(dfmat_matched, "Orgpurposecharitable")
predicted_class <- predict(train_results, newdata = dfmat_matched)
tab_class <- prop.table(table(actual_class, predicted_class))
tab_class


```
A confusion matrix from the caret package can give us additional detail to evaluate the outcome

```{r, echo=TRUE}
confusionMatrix(tab_class, mode = "everything")


```
We can convert the confusion matrix to a data frame and then combine it with tests for other organization purposes to compare the models for different classifications

```{r, echo=TRUE}
cm <- confusionMatrix(tab_class, mode = "everything")
tocsv<-as.data.frame(t(data.frame(cbind(t(cm$byClass),t(cm$overall)))))

```


```{r, echo=FALSE}

others <- dat[,c("Incorporatedstate","Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposereligious")]
dat2 <- cbind(dat2, others)

set.seed(300)
id_train <- sample(1:nrow(dat2), 1000, replace = FALSE)

dat2$id_numeric <- 1:nrow(dat2)
dat.corpus <- data.frame(lapply(dat2, as.character), stringsAsFactors=FALSE)
dat.corpus <- corpus(dat.corpus, 
                     text_field = "Corpus")

dfmat_training <- corpus_subset(dat.corpus, id_numeric %in% id_train) %>%
  dfm(stem = TRUE)
dfmat_test <- corpus_subset(dat.corpus, !id_numeric %in% id_train) %>%
  dfm(stem = TRUE)

tmod_nb <- textmodel_nb(dfmat_training, docvars(dfmat_training, "Orgpurposereligious"))
dfmat_matched <- dfm_select(dfmat_test, pattern=dfmat_training, selection = "keep")

actual_class <- docvars(dfmat_matched, "Orgpurposereligious")
predicted_class <- predict(tmod_nb, newdata = dfmat_matched)
tab_class <- prop.table(table(actual_class, predicted_class))
cm <- confusionMatrix(tab_class, mode = "everything")
tocsv <-cbind(tocsv, as.data.frame(t(data.frame(cbind(t(cm$byClass),t(cm$overall))))))


####Orgpurposeeducational




others <- dat[,c("Incorporatedstate","Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposeeducational")]
dat2 <- cbind(dat2, others)

set.seed(1500)
id_train <- sample(1:nrow(dat2), 1500, replace = FALSE)

dat2$id_numeric <- 1:nrow(dat2)
dat.corpus <- data.frame(lapply(dat2, as.character), stringsAsFactors=FALSE)
dat.corpus <- corpus(dat.corpus, 
                     text_field = "Corpus")

dfmat_training <- corpus_subset(dat.corpus, id_numeric %in% id_train) %>%
  dfm(stem = TRUE)
dfmat_test <- corpus_subset(dat.corpus, !id_numeric %in% id_train) %>%
  dfm(stem = TRUE)

tmod_nb <- textmodel_nb(dfmat_training, docvars(dfmat_training, "Orgpurposeeducational"))
dfmat_matched <- dfm_select(dfmat_test, pattern=dfmat_training, selection = "keep")

actual_class <- docvars(dfmat_matched, "Orgpurposeeducational")
predicted_class <- predict(tmod_nb, newdata = dfmat_matched)
tab_class <- prop.table(table(actual_class, predicted_class))
cm <- confusionMatrix(tab_class, mode = "everything")
tocsv <-cbind(tocsv, as.data.frame(t(data.frame(cbind(t(cm$byClass),t(cm$overall))))))

###Orgpurposescientific



others <- dat[,c("Incorporatedstate","Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposescientific")]
dat2 <- cbind(dat2, others)

set.seed(1500)
id_train <- sample(1:nrow(dat2), 1500, replace = FALSE)

dat2$id_numeric <- 1:nrow(dat2)
dat.corpus <- data.frame(lapply(dat2, as.character), stringsAsFactors=FALSE)
dat.corpus <- corpus(dat.corpus, 
                     text_field = "Corpus")

dfmat_training <- corpus_subset(dat.corpus, id_numeric %in% id_train) %>%
  dfm(stem = TRUE)
dfmat_test <- corpus_subset(dat.corpus, !id_numeric %in% id_train) %>%
  dfm(stem = TRUE)

tmod_nb <- textmodel_nb(dfmat_training, docvars(dfmat_training, "Orgpurposescientific"))
dfmat_matched <- dfm_select(dfmat_test, pattern=dfmat_training, selection = "keep")

actual_class <- docvars(dfmat_matched, "Orgpurposescientific")
predicted_class <- predict(tmod_nb, newdata = dfmat_matched)
tab_class <- prop.table(table(actual_class, predicted_class))
cm <- confusionMatrix(tab_class, mode = "everything")
tocsv <-cbind(tocsv, as.data.frame(t(data.frame(cbind(t(cm$byClass),t(cm$overall))))))



#Orgpurposeliterary



others <- dat[,c("Incorporatedstate","Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposeliterary")]
dat2 <- cbind(dat2, others)

set.seed(1500)
id_train <- sample(1:nrow(dat2), 1500, replace = FALSE)

dat2$id_numeric <- 1:nrow(dat2)
dat.corpus <- data.frame(lapply(dat2, as.character), stringsAsFactors=FALSE)
dat.corpus <- corpus(dat.corpus, 
                     text_field = "Corpus")

dfmat_training <- corpus_subset(dat.corpus, id_numeric %in% id_train) %>%
  dfm(stem = TRUE)
dfmat_test <- corpus_subset(dat.corpus, !id_numeric %in% id_train) %>%
  dfm(stem = TRUE)

tmod_nb <- textmodel_nb(dfmat_training, docvars(dfmat_training, "Orgpurposeliterary"))
dfmat_matched <- dfm_select(dfmat_test, pattern=dfmat_training, selection = "keep")

actual_class <- docvars(dfmat_matched, "Orgpurposeliterary")
predicted_class <- predict(tmod_nb, newdata = dfmat_matched)
tab_class <- prop.table(table(actual_class, predicted_class))
cm <- confusionMatrix(tab_class, mode = "everything")
tocsv <-cbind(tocsv, as.data.frame(t(data.frame(cbind(t(cm$byClass),t(cm$overall))))))



###Orgpurposepublicsafety



others <- dat[,c("Incorporatedstate","Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposepublicsafety")]
dat2 <- cbind(dat2, others)

set.seed(1500)
id_train <- sample(1:nrow(dat2), 1500, replace = FALSE)

dat2$id_numeric <- 1:nrow(dat2)
dat.corpus <- data.frame(lapply(dat2, as.character), stringsAsFactors=FALSE)
dat.corpus <- corpus(dat.corpus, 
                     text_field = "Corpus")

dfmat_training <- corpus_subset(dat.corpus, id_numeric %in% id_train) %>%
  dfm(stem = TRUE)
dfmat_test <- corpus_subset(dat.corpus, !id_numeric %in% id_train) %>%
  dfm(stem = TRUE)

tmod_nb <- textmodel_nb(dfmat_training, docvars(dfmat_training, "Orgpurposepublicsafety"))
dfmat_matched <- dfm_select(dfmat_test, pattern=dfmat_training, selection = "keep")

actual_class <- docvars(dfmat_matched, "Orgpurposepublicsafety")
predicted_class <- predict(tmod_nb, newdata = dfmat_matched)
tab_class <- prop.table(table(actual_class, predicted_class))
cm <- confusionMatrix(tab_class, mode = "everything")
tocsv <-cbind(tocsv, as.data.frame(t(data.frame(cbind(t(cm$byClass),t(cm$overall))))))

####Orgpurposeamateursports


others <- dat[,c("Incorporatedstate","Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposeamateursports")]
dat2 <- cbind(dat2, others)

set.seed(1500)
id_train <- sample(1:nrow(dat2), 1500, replace = FALSE)

dat2$id_numeric <- 1:nrow(dat2)
dat.corpus <- data.frame(lapply(dat2, as.character), stringsAsFactors=FALSE)
dat.corpus <- corpus(dat.corpus, 
                     text_field = "Corpus")

dfmat_training <- corpus_subset(dat.corpus, id_numeric %in% id_train) %>%
  dfm(stem = TRUE)
dfmat_test <- corpus_subset(dat.corpus, !id_numeric %in% id_train) %>%
  dfm(stem = TRUE)

tmod_nb <- textmodel_nb(dfmat_training, docvars(dfmat_training, "Orgpurposeamateursports"))
dfmat_matched <- dfm_select(dfmat_test, pattern=dfmat_training, selection = "keep")

actual_class <- docvars(dfmat_matched, "Orgpurposeamateursports")
predicted_class <- predict(tmod_nb, newdata = dfmat_matched)
tab_class <- prop.table(table(actual_class, predicted_class))
cm <- confusionMatrix(tab_class, mode = "everything")
tocsv <-cbind(tocsv, as.data.frame(t(data.frame(cbind(t(cm$byClass),t(cm$overall))))))

####Orgpurposecrueltyprevention


others <- dat[,c("Incorporatedstate","Donatefundsyes","Onethirdsupportpublic","Onethirdsupportgifts",
                 "Disasterreliefyes", "Orgpurposecrueltyprevention")]
dat2 <- cbind(dat2, others)

set.seed(1500)
id_train <- sample(1:nrow(dat2), 1500, replace = FALSE)

dat2$id_numeric <- 1:nrow(dat2)
dat.corpus <- data.frame(lapply(dat2, as.character), stringsAsFactors=FALSE)
dat.corpus <- corpus(dat.corpus, 
                     text_field = "Corpus")

dfmat_training <- corpus_subset(dat.corpus, id_numeric %in% id_train) %>%
  dfm(stem = TRUE)
dfmat_test <- corpus_subset(dat.corpus, !id_numeric %in% id_train) %>%
  dfm(stem = TRUE)

tmod_nb <- textmodel_nb(dfmat_training, docvars(dfmat_training, "Orgpurposecrueltyprevention"))
dfmat_matched <- dfm_select(dfmat_test, pattern=dfmat_training, selection = "keep")

actual_class <- docvars(dfmat_matched, "Orgpurposecrueltyprevention")
predicted_class <- predict(tmod_nb, newdata = dfmat_matched)
tab_class <- prop.table(table(actual_class, predicted_class))
cm <- confusionMatrix(tab_class, mode = "everything")
tocsv <-cbind(tocsv, as.data.frame(t(data.frame(cbind(t(cm$byClass),t(cm$overall))))))

colnames(tocsv) <- c("Charity", "Religious", "Education", "Scientific", "Literary", "Safety", "Sports", "Cruelty")
                   

```

We can rerun that code using the other organization purposes in the data, and combine them into a data frame to compare the sucess of the naive bayes

```{r, echo=TRUE}
pandoc.table(tocsv)
```

Credit to the tutorials on the Quanteda website, where much of this was originally learned