---
title: "Roles and Responsibilities"
author: "David Selby"
date: "7/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( echo = TRUE, message=F, warning=F, cache = F )
```

## Required Packages
```{r}
require( dplyr )
require( pander )
require( stringr )
require( hunspell )

```


## Load Data

```{r}
d2 <- readRDS( "Data/categorized-titles.rds")

```


##  Seperates Roles and Responsiblities

Find the Most Common Words that Indicate Role

1. Address executive titles
2. Seperate unambigious roles from responsibilities
3. Seperate ambigious roles from responsibilities using logical opperators
4. Clean up Extra Spaces
5. Check 25 Random Titles




```{r}
Role.Dictionary <-  c(
" PAST ", " FORMER ", " INTERIM ", " SENIOR ", " DIRECTOR ", " DEPUTY ", " TRUSTEE ", " MANAGER "," MGR ", " MANAGEMENT ", " HEAD ", " COORDINATOR ", " CO ", " TRUSTEE ", " SENIOR VICE PRESIDENT ", " EXECUTIVE VICE ", " DEAN ", " ASSISTANT ", " ASSOCIATE ", " EXECUTIVE VICE PRESIDENT ", " VICE ", " ASSOCIATE ", " SUPERVISING ", " PRESIDENT ", " HEAD_START ")
Role.Dictionary
```

## Executive titles

Title                        Role              Responsibility
-----------------------     ----------------   ----------------
Chief Executive OFFicer      Chief Officer      Cheif Executive Officer
CEO                          Chief Officer      CEO
Chief Finiancial Officer     Chief Officer      Chief Finiancial Officer
CFO                          Chief Officer      CFO


```{r}
d2$TitleRole <- "  "
d2$TitleResp <- d2$TitleTxt2

d2$TitleResp <- str_c( " ",d2$TitleResp )
d2$TitleResp <- str_c( d2$TitleResp," " )

# REPLACE
# d2$TitleResp <- gsub( " VICE PRESIDENT ", " VICE#PRESIDENT ", d2$TitleResp )
# d2$TitleResp <- gsub( " EXECUTIVE DIRECTOR ", " EXECUTIVE_DIRECTOR ", d2$TitleResp )
# d2$TitleResp <- gsub( " HEAD START ", " HEAD_START ", d2$TitleResp )

#Chief Executive
d2$TitleRole[ grepl( " CHIEF ", d2$TitleResp ) & grepl( " EXECUTIVE ", d2$TitleResp ) ] <- " CHIEF EXECUTIVE "
d2$TitleRole[ grepl( " CHIEF ", d2$TitleResp ) & grepl( " OFFICER ", d2$TitleResp ) ] <- " CHIEF OFFICER "
d2$TitleRole[ grepl( " CHIEF ", d2$TitleResp ) & !grepl( " OFFICER ", d2$TitleResp ) ] <- " CHIEF "
d2$TitleResp[ grepl( " CHIEF ", d2$TitleResp ) & !grepl( " OFFICER ", d2$TitleResp ) ] <- (gsub( " CHIEF ", " ", d2$TitleResp))[ grepl( " CHIEF ", d2$TitleResp ) & !grepl( " OFFICER ", d2$TitleResp ) ]

d2$TitleRole[ grepl( " C[A-Z]O ", d2$TitleResp) ] <- " CHIEF OFFICER "

#EXECUTIVE DIRECTOR
d2$TitleRole[ grepl( " EXECUTIVE DIRECTOR ", d2$TitleResp ) ] <- paste(d2$TitleRole, " EXECUTIVE DIRECTOR ", sep ="")[ grepl( " EXECUTIVE DIRECTOR ", d2$TitleResp ) ]
d2$TitleResp <- gsub( "EXECUTIVE DIRECTOR ", " ", d2$TitleResp)
```



## Clear Titles

```{r}
#PAST
d2$TitleRole[ grepl( " PAST ", d2$TitleResp) ] <- paste(d2$TitleRole, " PAST ", sep ="")[ grepl( " PAST ", d2$TitleResp) ]
d2$TitleResp <- gsub( "PAST", " ", d2$TitleResp)

#FORMER
d2$TitleRole[ grepl( " FORMER ", d2$ TitleResp) ] <- paste(d2$TitleRole, " FORMER ", sep ="")[ grepl( " FORMER ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " FORMER ", " ", d2$TitleResp)

#INTERIM
d2$TitleRole[ grepl( " INTERIM ", d2$ TitleResp) ] <- paste(d2$TitleRole, " INTERIM ", sep ="")[ grepl( " INTERIM ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " INTERIM ", " ", d2$TitleResp)

#" CO "
d2$TitleRole[ grepl( " CO ", d2$ TitleResp) ] <- paste(d2$TitleRole, " CO ", sep ="")[ grepl( " CO ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " CO ", " ", d2$TitleResp)

d2$TitleRole[ grepl( " FOUNDER ", d2$ TitleResp) ] <- paste(d2$TitleRole, " FOUNDER ", sep ="")[ grepl( " FOUNDER ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " FOUNDER ", " ", d2$TitleResp)


#Executive Senior Vice President
d2$TitleRole[ grepl( " EXECUTIVE SENIOR VICE PRESIDENT ", d2$ TitleResp) ] <- paste(d2$TitleRole, " EXECUTIVE SENIOR VICE PRESIDENT ", sep ="")[ grepl( " EXECUTIVE SENIOR VICE PRESIDENT ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " EXECUTIVE SENIOR VICE PRESIDENT ", " ", d2$TitleResp)

#Senior Executive Vice President
d2$TitleRole[ grepl( " SENIOR EXECUTIVE VICE PRESIDENT ", d2$ TitleResp) ] <- paste(d2$TitleRole, " SENIOR EXECUTIVE VICE PRESIDENT ", sep ="")[ grepl( " SENIOR EXECUTIVE VICE PRESIDENT ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " SENIOR EXECUTIVE VICE PRESIDENT ", " ", d2$TitleResp)

# Senior Vice President
d2$TitleRole[ grepl( " SENIOR VICE PRESIDENT ", d2$ TitleResp) ] <- paste(d2$TitleRole, " SENIOR VICE PRESIDENT ", sep ="")[ grepl( " SENIOR VICE PRESIDENT ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " SENIOR VICE PRESIDENT ", " ", d2$TitleResp)

# Executive Vice President
d2$TitleRole[ grepl( " EXECUTIVE VICE PRESIDENT ", d2$ TitleResp) ] <- paste(d2$TitleRole, " EXECUTIVE VICE PRESIDENT ", sep ="")[ grepl( " EXECUTIVE VICE PRESIDENT ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " EXECUTIVE VICE PRESIDENT ", " ", d2$TitleResp)

# Vice President
d2$TitleRole[ grepl( " VICE PRESIDENT ", d2$ TitleResp) ] <- paste(d2$TitleRole, " VICE PRESIDENT ", sep ="")[ grepl( " VICE PRESIDENT ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " VICE PRESIDENT ", " ", d2$TitleResp)

#Senior 
d2$TitleRole[ grepl( " SENIOR ", d2$ TitleResp) ] <- paste(d2$TitleRole, " SENIOR ", sep ="")[ grepl( " SENIOR ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " SENIOR ", " ", d2$TitleResp)

# DEPUTY
d2$TitleRole[ grepl( " DEPUTY ", d2$ TitleResp) ] <- paste(d2$TitleRole, " DEPUTY ", sep ="")[ grepl( " DEPUTY ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " DEPUTY ", " ", d2$TitleResp)

#President
d2$TitleRole[ grepl( " PRESIDENT ", d2$ TitleResp) ] <- paste(d2$TitleRole, " PRESIDENT ", sep ="")[ grepl( " PRESIDENT ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " PRESIDENT ", " ", d2$TitleResp)

#" TRUSTEE ",
d2$TitleRole[ grepl( " TRUSTEE ", d2$ TitleResp) ] <- paste(d2$TitleRole, " TRUSTEE ", sep ="")[ grepl( " TRUSTEE ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " TRUSTEE ", " ", d2$TitleResp)

#" MANAGER ",
d2$TitleRole[ grepl( " MANAGER ", d2$ TitleResp) ] <- paste(d2$TitleRole, " MANAGER ", sep ="")[ grepl( " MANAGER ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " MANAGER ", " ", d2$TitleResp)

#" MANAGEMENT "
d2$TitleRole[ grepl( " MANAGEMENT ", d2$ TitleResp) ] <- paste(d2$TitleRole, " MANAGEMENT ", sep ="")[ grepl( " MANAGEMENT ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " MANAGEMENT ", " ", d2$TitleResp)

#" COORDINATOR "
d2$TitleRole[ grepl( " COORDINATOR ", d2$ TitleResp) ] <- paste(d2$TitleRole, " COORDINATOR ", sep ="")[ grepl( " COORDINATOR ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " COORDINATOR ", " ", d2$TitleResp)

#" DEAN " 
d2$TitleRole[ grepl( " DEAN ", d2$ TitleResp) ] <- paste(d2$TitleRole, " DEAN ", sep ="")[ grepl( " DEAN ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " DEAN ", " ", d2$TitleResp)

#" SUPERVISING "
d2$TitleRole[ grepl( " SUPERVISING ", d2$ TitleResp) ] <- paste(d2$TitleRole, " SUPERVISING ", sep ="")[ grepl( " SUPERVISING ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " SUPERVISING ", " ", d2$TitleResp)

#" DEPARTMENT CHAIR "
d2$TitleRole[ grepl( " DEPARTMENT CHAIR ", d2$ TitleResp) ] <- paste(d2$TitleRole, " DEPARTMENT CHAIR ", sep ="")[ grepl( " DEPARTMENT CHAIR ", d2$ TitleResp) ]
d2$TitleResp <- gsub( " DEPARTMENT CHAIR ", " ", d2$TitleResp)

```

## Titles that need logical Operators

```{r}
# Executive
d2$TitleRole[ grepl( " EXECUTIVE ", d2$ TitleResp ) & !grepl( " CHIEF ", d2$TitleResp )  & !grepl( " EXECUTIVE DIRECTOR ", d2$TitleResp ) & d2$ADMIN.SUP != 1 ] <- paste(d2$TitleRole, " EXECUTIVE ", sep ="")[ grepl( " EXECUTIVE ", d2$TitleResp ) & !grepl( " CHIEF ", d2$TitleResp )  & !grepl( " EXECUTIVE DIRECTOR ", d2$TitleResp ) & d2$ADMIN.SUP != 1 ]

d2$TitleResp[ grepl( " EXECUTIVE ", d2$ TitleResp ) & !grepl( " CHIEF ", d2$TitleResp )  & !grepl( " EXECUTIVE DIRECTOR ", d2$TitleResp ) & d2$ADMIN.SUP != 1 ] <- gsub( " EXECUTIVE ", " ",  d2$TitleResp )[ grepl( " EXECUTIVE ", d2$ TitleResp ) & !grepl( " CHIEF ", d2$TitleResp )  & !grepl( " EXECUTIVE DIRECTOR ", d2$TitleResp ) & d2$ADMIN.SUP != 1 ]

# DIRECTOR
d2$TitleRole[ grepl( " DIRECTOR ", d2$ TitleResp ) &  !grepl( " EXECUTIVE ", d2$TitleResp ) ] <- paste(d2$TitleRole, " DIRECTOR ", sep ="")[ grepl( " DIRECTOR ", d2$ TitleResp ) &  !grepl( " EXECUTIVE ", d2$TitleResp ) ]
d2$TitleResp[ grepl( " DIRECTOR ", d2$ TitleResp ) &  !grepl( " EXECUTIVE ", d2$TitleResp ) ] <- gsub( " DIRECTOR ", " ", d2$TitleResp )[ grepl( " DIRECTOR ", d2$ TitleResp ) &  !grepl( " EXECUTIVE ", d2$TitleResp ) ]


# ASSISTANT Only if not Administrative Support
d2$TitleRole[ grepl( " ASSISTANT ", d2$ TitleResp ) & d2$ADMIN.SUP != 1 ] <- paste(d2$TitleRole, " ASSISTANT ", sep ="")[ grepl( " ASSISTANT ", d2$ TitleResp ) & d2$ADMIN.SUP != 1 ]
d2$TitleResp[ grepl( " ASSISTANT ", d2$ TitleResp ) & d2$ADMIN.SUP != 1 ] <- gsub( " ASSISTANT ", " ", d2$TitleResp)[ grepl( " ASSISTANT ", d2$ TitleResp ) & d2$ADMIN.SUP != 1 ]

# ASSOCIATE  Only if not Administrative Support
d2$TitleRole[ grepl( " ASSOCIATE ", d2$ TitleResp ) & d2$ADMIN.SUP != 1 ] <- paste(d2$TitleRole, " ASSOCIATE ", sep ="")[ grepl( " ASSOCIATE ", d2$ TitleResp ) & d2$ADMIN.SUP != 1 ]
d2$TitleResp[ grepl( " ASSOCIATE ", d2$ TitleResp ) & d2$ADMIN.SUP != 1 ] <- gsub( " ASSOCIATE ", " ", d2$TitleResp)[ grepl( " ASSOCIATE ", d2$ TitleResp ) & d2$ADMIN.SUP != 1 ]

Title.Test <- cbind(as.character(d2$TitleTxt), d2$TitleTxt2, d2$TitleRole, d2$TitleResp ) %>% as.data.frame() 
colnames(Title.Test) <- c("Title", "Cleaned Title", "Role", "Responsibilty")

#DIVISION HEAD
d2$TitleRole[ grepl( " DIVISION HEAD ", d2$ TitleResp ) ] <- paste(d2$TitleRole, " DIVISION HEAD ", sep ="")[ grepl( " DIVISION HEAD ", d2$ TitleResp )]
d2$TitleResp[ grepl( " DIVISION HEAD ", d2$ TitleResp ) ] <- gsub( " DIVISION HEAD ", " ", d2$TitleResp)[ grepl( " DIVISION HEAD ", d2$ TitleResp )]

#" HEAD "
d2$TitleRole[ grepl( " HEAD ", d2$TitleResp) & !grepl( " HEAD START ", d2$ TitleResp) & !grepl(" MASTER ", d2$TitleResp) & !grepl(" SCHOOL ", d2$TitleResp)  ] <- paste(d2$TitleRole, " HEAD ", sep ="")[ grepl( " HEAD ", d2$TitleResp) & !grepl( " HEAD START ", d2$ TitleResp) & !grepl(" MASTER ", d2$TitleResp) & !grepl(" SCHOOL ", d2$TitleResp)  ]
d2$TitleResp[ grepl( " HEAD ", d2$TitleResp) & !grepl( " HEAD START ", d2$ TitleResp) & !grepl(" MASTER ", d2$TitleResp) & !grepl(" SCHOOL ", d2$TitleResp)  ] <- gsub( " HEAD ", " ", d2$TitleResp )[ grepl( " HEAD ", d2$TitleResp) & !grepl( " HEAD START ", d2$ TitleResp) & !grepl(" MASTER ", d2$TitleResp) & !grepl(" SCHOOL ", d2$TitleResp ) ]
```

## Remove Extra Spaces from Titles

```{r}
d2$TitleResp <- gsub( "  ", " ", d2$TitleResp )
d2$TitleResp <- gsub( "  ", " ", d2$TitleResp )
d2$TitleResp <- gsub( "  ", " ", d2$TitleResp )
d2$TitleResp <- gsub( "  ", " ", d2$TitleResp )
d2$TitleResp <- gsub( "  ", " ", d2$TitleResp )
d2$TitleResp <- gsub( "  ", " ", d2$TitleResp )
d2$TitleResp <- gsub( "  ", " ", d2$TitleResp )
d2$TitleResp <- gsub( "  ", " ", d2$TitleResp )


d2$TitleRole <- gsub( "  ", " ", d2$TitleRole )
d2$TitleRole <- gsub( "  ", " ", d2$TitleRole )
d2$TitleRole <- gsub( "  ", " ", d2$TitleRole )
d2$TitleRole <- gsub( "  ", " ", d2$TitleRole )
d2$TitleRole <- gsub( "  ", " ", d2$TitleRole )
d2$TitleRole <- gsub( "  ", " ", d2$TitleRole )
d2$TitleRole <- gsub( "  ", " ", d2$TitleRole )
d2$TitleRole <- gsub( "  ", " ", d2$TitleRole )
                                                                                                  
	 
```


## Check 25 Random Titles

```{r}
Title.Test <- cbind(as.character(d2$TitleTxt), d2$TitleTxt2, d2$TitleRole, d2$TitleResp ) %>% as.data.frame() 
colnames(Title.Test) <- c("Title", "Cleaned Title", "Role", "Responsibilty")

set.seed(100)
ii<-sample(1:nrow(d2), 25 )
Title.Test[ii,] %>% knitr::kable()

```

## Save

```{r}

saveRDS( d2, "Data/roles-and-responsibility.rds")

```
