---
title: "Title Categories Top 1000"
author: "David Selby"
date: "6/18/2019"
output:
 html_document:
 toc: true
 toc_depth: 1
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Required Packages

``` {r}
library(tidyverse)
library(reshape2)
library( dplyr )
library( pander )
library( stringr )
library( hunspell )

```

# Catagories {.tabset}

Variable Name	        Category Name               
--------------       --------------			          
CEO	                  Chief Executive		          
CFO	                  Financial				            
Treasurer	            Treasurer				            
DEP.CEO	              Deputy Chief Executive		  
SEC	                  Secretary				            
COO	                  Operations				          
TRUST	                Trustee/Board				        
HUM.RES	              Human Resources				      
DEP.HEAD	            Department Head				      
MAN	Generic           Management				          
DEV	                  Development				          
TECH	                Technology/IT				        
COMM	                Communications				      
OTHER	                Other Category				      
PROJECT	              Project Manager				      
LEGAL	                Legal				           		  
FACILITIES            Facilities				          
ADMIN.SUP	            Administrative Support		  
MED.MAN	              Medical Management				  
HEALTH.HUM	          Health and Human Services		
TRAIN	                Training/Education		      
ACADEMIC.MAN	        Academic Manager				    
PROFESIONAL	          Professional				        
OTHER.PROF	          Other Professional				  
ACADEMIC.PROF	        Academic Professional		    
MED.PROF	            Medical Professional			  



## CEO

```{r CEO}
CEO<- c(
" EXECUTIVE DIRECTOR ", 
" PRESIDENT ", 
" PRESIDENT CEO ", 
" CEO ", 
" CHIEF EXECUTIVE OFFICER ", 
" HEAD SCHOOL ", 
" PRESIDENTCEO ", 
" PRINCIPAL ", 
" PRESIDENT DIRECTOR ", 
" FORMER EXECUTIVE DIRECTOR ", 
" HEADMASTER ", 
" CEO PRESIDENT ", 
" PRESIDENT EXECUTIVE DIRECTOR ", 
" EXECUTIVE DIRECTOR CEO ", 
" PRESIDENT CE ", 
" INTERIM EXECUTIVE DIRECTOR ", 
" CO EXECUTIVE DIRECTOR ", 
" EXECUTIVE DIRECTOR ", 
" PRESIDENT ", 
" PRESIDENT CEO ", 
" CEO ", 
" CHIEF EXECUTIVE OFFICER ", 
" HEAD SCHOOL ", 
" PRESIDENTCEO ", 
" PRINCIPAL ", 
" PRESIDENT DIRECTOR ", 
" FORMER EXECUTIVE DIRECTOR ", 
" HEADMASTER ", 
" CEO PRESIDENT ", 
" PRESIDENT EXECUTIVE DIRECTOR ", 
" EXECUTIVE DIRECTOR CEO ", 
" PRESIDENT CE ", 
" INTERIM EXECUTIVE DIRECTOR ", 
" CO EXECUTIVE DIRECTOR ", 
" EXECUTIVE DIRECTOR SECRETARY ", 
" PRESIDENT TREASURER ", 
" SUPERINTENDENT ", 
" SCOUT EXECUTIVE ", 
" SCHOOL DIRECTOR ", 
" FORMER PRESIDENT ", 
" DIRECTOR PRESIDENT ", 
" EXECUTIVE DIRECTOR PRESIDENT ", 
" CEO EXECUTIVE DIRECTOR ", 
" FORMER CEO ", 
" SECRETARY EXECUTIVE DIRECTOR ", 
" FORMER PRESIDENT CEO ", 
" PAST EXECUTIVE DIRECTOR ", 
" PRESIDENT TRUSTEE ", 
" INTERIM CEO ", 
" CHIEF EXECUTIVE ", 
" TRUSTEE PRESIDENT CEO ", 
" CEO DIRECTOR ", 
" DIRECTOR PRESIDENT CEO ", 
" FORMER EXECUTIVE ", 
" PRESIDENT CEO DIRECTOR ", 
" DIRECTOR CEO ", 
" CAMP DIRECTOR ", 
" PRESIDENT SECRETARY ", 
" PRESIDENT COO ", 
" BOARD DIRECTOR ", 
" INTERIM PRESIDENT ", 
" HEAD COACH ", 
" EXECUTIVE DIRECTOR FORMER ", 
" CHIEF ", 
" EXECUTIVE DIRECTOR THRU ", 
" CHAIR CEO ", 
" EXECUTIVE OFFICER ", 
" PRESIDENT CHIEF EXECUTIVE OFFICER ", 
" CEO ADMINISTRATOR ", 
" CEO ADMINISTRATION ", 
" GENERAL DIRECTOR ", 
" VICE PRESIDENT EXECUTIVE DIRECTOR ", 
" CHANCELLOR ", 
" MANAGING ATTORNEY ", 
" TRUSTEE PRESIDENT ", 
" EXECUTIVE DIRECTOR TREASURER ", 
" MUSEUM DIRECTOR ", 
" CEO SECRETARY ", 
" PRESIDENT AN ", 
" EXECUTIVE ", 
" PRESIDENT CHAIR ", 
" EXECUTIVE DIRECTOR UNTIL ", 
" CEOPRESIDENT ", 
" INTERIM EXECUTIVE ", 
" PRESIDENT EX OFFICER ", 
" EXECUTIVE DIRECTOR THROUGH ", 
" ACTING EXECUTIVE DIRECTOR ", 
" PAST PRESIDENT ", 
" CO PRESIDENT ", 
" CHAIR PRESIDENT ", 
" PRESIDENT CHIEF EXECUTIVE OFFICER ", 
" PRESIDENT CEO TRUSTEE ", 
" INTERIM DIRECTOR ", 
" EXECUTIVE DIRECTOR PART YEAR ", 
" GENERAL MGR ", 
" PRESIDENT CEO EX OFFICER ", 
" PRESIDENT CHIEF EXECUTIVE ", 
" EXECUTIVE DIRECTOR EX OFFICER ", 
" PRESIDENTDIRECTOR ", 
" PRESIDENTEXECUTIVE DIRECTOR ", 
" PRIOR EXECUTIVE DIRECTOR ", 
" PRESIDENT EMERITUS ", 
" PRESIDENT EX ", 
" PRESIDENT FOUNDER ", 
" DIRECTOR EXECUTIVE DIRECTOR ", 
" CHIEF EXECUTIVE O ", 
" EXECUTIVE PRODUCER ", 
" FOUNDER CEO ", 
" MIDDLE SCHOOL PRINCIPAL ", 
" SCHOOL PRINCIPAL ", 
" UPPER SCHOOL HEAD ", 
" EXECUTIVE DIRECTOR PHYSICIAN ", 
" BOARD MEMBER EXECUTIVE DIRECTOR ", 
" EDITOR IN CHIEF ", 
" BOARD MEMBER CEO ", 
" INTERIM PRESIDENT CEO ", 
" FORMER HEAD SCHOOL ", 
" EXECUTIVE DIRECTOR VICE PRESIDENT ", 
" PRESIDENT CEO SECRETARY ", 
" FOUNDATION PRESIDENT ", 
" SECRETARY CEO ", 
" ADMINISTRATOR CEO ", 
" EXECUTIVE VICE PRESIDENT CEO ", 
" SCOUT EXECUTIVE CEO ", 
" CEO BOARD MEMBER ", 
" CHIEF EXECUTIVE DIRECTOR ", 
" EXECUTIVE DIRECTOR", 
" FOUNDER PRESIDENT ", 
" CHAPTER PRESIDENT ", 
" CEO THROUGH ", 
" CEO THRU ", 
" MIDDLE SCHOOL HEAD ", 
" EX OFFICER DIRECTOR ", 
" EXECUTIVE DIRECTOR DIRECTOR ", 
" REGIONAL EXECUTIVE DIRECTOR ", 
" FORMER CHIEF EXECUTIVE OFFICER ", 
" HIGH SCHOOL PRINCIPAL ", 
" LOWER SCHOOL HEAD ", 
" CEO FOUNDER ", 
" CHAIR DIRECTOR ", 
" EXECUTIVE DIRECTOR BOARD MEMBER ", 
" EXECUTIVE EDITOR ", 
" HEAD MASTER ", 
" FOUNDER EXECUTIVE DIRECTOR ", 
" MIDDLE SCHOOL DIRECTOR ", 
" PRESIDENT CEO THRU ", 
" TREASURER EXECUTIVE DIRECTOR ", 
" PRINCIPAL DIRECTOR ", 
" UPPER SCHOOL DIRECTOR ", 
" CEO CHAIR ", 
" CEO PRINCIPAL ", 
" HOSPITAL PRESIDENT ", 
" PRESIDENTTREASURER ", 
" PRESIDENT TREASURER DIRECTOR ", 
" DIRECTOR UPPER SCHOOL ", 
" EXECUTIVE DIRECTOR TRUSTEE ", 
" PRESIDENTCHIEF EXECUTIVE OFFICER ", 
" TRUSTEE EXECUTIVE DIRECTOR ", 
" UPPER SCHOOL PRINCIPAL ", 
" CO CEO ", 
" DIRECTOR MIDDLE SCHOOL ", 
" INTERIM HEAD SCHOOL ", 
" LOWER SCHOOL PRINCIPAL ", 
" PRESIDENT CPO ", 
" CURRENT EXECUTIVE DIRECTOR ", 
" VICE CHAIR CEO ", 
" EXECUTIVE DIRECTOR FROM ", 
" UNIVERSITY PRESIDENT ", 
" CEO TRUSTEE ", 
" DIRECTOR LOWER SCHOOL ", 
" EXECUTIVE DIRECTOR CFO ", 
" EXECUTIVE DIRECTOR CURRENT ", 
" EXECUTIVE DIRECTOR FOUNDATION ", 
" LOWER SCHOOL DIRECTOR ", 
" PAST CEO ", 
" PRESIDENTTRUSTEE ", 
" PRESIDENT C ", 
" CEO FORMER ", 
" FORMER PRESIDENTCEO ", 
" PRESIDENT THRU ", 
" BOARD MEMBER PRESIDENT CEO ", 
" EXECUTIVE DIRECTOR AS ", 
" EXECUTIVE DIRECTOR RETIRED ", 
" PRESIDENT THROUGH ", 
" BRANCH EXECUTIVE DIRECTOR ", 
" DIRECTOR CHAIR ", 
" PRESIDENT ADMINISTRATOR ", 
" PRESIDENT CEO UNTIL ", 
" BOARD MEMBER PRESIDENT ", 
" EXECUTIVE DIRECTOR PARTIAL YEAR ", 
" BOARD PRESIDENT ", 
" PRESIDENT FOUNDATION ", 
" HEAD SCHOOLS ", 
" PRESIDENT CEO BOARD MEMBER ", 
" COLLEGE PRESIDENT ", 
" DIRECTOR PRINCIPAL ", 
" EXECDIRECTOR ", 
" PRESIDENT CFO ", 
" PRESIDENT FORMER ", 
" PRESIDENT UNTIL ", 
" SCHOOL LEADER ", 
" SENIOR VICE PRESIDENT SECRETARY ",
" CEO",
" PRESIDENT CEO") 

CEO <- unique(CEO)

```


## CEO Problems

HEAD SCHOOL

CAMP DIRECTOR
GENERAL MGR


```{r CEO Problems}

CEO.Prob <- c(
" SCOUT EXECUTIVE ", 
" SCHOOL DIRECTOR ", 
" BOARD DIRECTOR ", 
" HEAD COACH ", 
" CHIEF ", 
" GENERAL DIRECTOR ", 
" VICE PRESIDENT EXECUTIVE DIRECTOR ", 
" MANAGING ATTORNEY ", 

" MUSEUM DIRECTOR ", 

" INTERIM DIRECTOR ", 
" PRESIDENT CEO EX OFFICER ", 
" PRESIDENT FOUNDER ", 
" MIDDLE SCHOOL PRINCIPAL ", 
" SCHOOL PRINCIPAL ", 
" UPPER SCHOOL HEAD ", 
" BOARD MEMBER EXECUTIVE DIRECTOR ", 
" EDITOR IN CHIEF ", 
" FORMER HEAD SCHOOL ", 
" CHAPTER PRESIDENT ", 
" MIDDLE SCHOOL HEAD ", 
" EX OFFICER DIRECTOR ", 
" REGIONAL EXECUTIVE DIRECTOR ", 
" HIGH SCHOOL PRINCIPAL ", 
" LOWER SCHOOL HEAD ", 
" CHAIR DIRECTOR ", 
" EXECUTIVE DIRECTOR BOARD MEMBER ", 
" EXECUTIVE EDITOR ", 
" HEAD MASTER ", 
" MIDDLE SCHOOL DIRECTOR ", 
" PRINCIPAL DIRECTOR ", 
" UPPER SCHOOL DIRECTOR ", 
" CEO CHAIR ", 
" DIRECTOR UPPER SCHOOL ", 

" UPPER SCHOOL PRINCIPAL ", 
" DIRECTOR MIDDLE SCHOOL ", 
" INTERIM HEAD SCHOOL ", 
" LOWER SCHOOL PRINCIPAL ", 

" DIRECTOR LOWER SCHOOL ", 
" LOWER SCHOOL DIRECTOR ", 
" BOARD MEMBER PRESIDENT CEO ", 
" EXECUTIVE DIRECTOR RETIRED ", 
" BRANCH EXECUTIVE DIRECTOR ", 
" DIRECTOR CHAIR ", 
" PRESIDENT ADMINISTRATOR ", 
" BOARD MEMBER PRESIDENT ", 
" BOARD PRESIDENT ", 
" HEAD SCHOOLS ", 
" COLLEGE PRESIDENT ", 
" DIRECTOR PRINCIPAL ", 
" SCHOOL LEADER ", 
" SENIOR VICE PRESIDENT SECRETARY ",
" EXECUTIVE DIRECTOR BOARD MEMBER ", 

" PRESIDENT CEO BOARD MEMBER ",
" HEAD SCHOOL ",
" HEADMASTER ",
" CAMP DIRECTOR ",
" GENERAL MGR ",
" MS PRINCIPAL "
)
CEO.Prob <- unique(CEO.Prob)

CEO.Board <-c(
" PRESIDENTTRUSTEE ", 
" EXECUTIVE DIRECTOR TRUSTEE ", 
" TRUSTEE EXECUTIVE DIRECTOR ", 
" VICE CHAIR CEO ", 
" CEO TRUSTEE ", 
" TRUSTEE PRESIDENT ", 
" PRESIDENT CEO TRUSTEE ") %>% unique



CEO.SCHOOL <- c(
" HEAD COACH ",
" MIDDLE SCHOOL PRINCIPAL ",
" SCHOOL PRINCIPAL ",
" UPPER SCHOOL HEAD ",
" MIDDLE SCHOOL HEAD ",
" REGIONAL EXECUTIVE DIRECTOR ",
" HIGH SCHOOL PRINCIPAL ",
" LOWER SCHOOL HEAD ",
" HEAD MASTER ",
" UPPER SCHOOL DIRECTOR ",
" DIRECTOR UPPER SCHOOL ",
" UPPER SCHOOL PRINCIPAL ",
" DIRECTOR MIDDLE SCHOOL ",
" INTERIM HEAD SCHOOL ",
" LOWER SCHOOL PRINCIPAL ",
" DIRECTOR LOWER SCHOOL ",
" LOWER SCHOOL DIRECTOR ",
" HEAD SCHOOLS ",
" SCHOOL LEADER ",
" SCHOOL DIRECTOR ",
" FORMER HEAD SCHOOL ",
" MIDDLE SCHOOL DIRECTOR ")

SCHOOL.HEAD <- c(
" ASSISTANT HEAD SCHOOL ",
" HEAD SCHOOL ",
" HEAD UPPER SCHOOL ",
" HEAD LOWER SCHOOL ",
" HEAD MIDDLE SCHOOL ",
" ASSOCIATE HEAD SCHOOL ",
" FORFORMER HEAD SCHOOL ",
" DIRECTOR COACHING ",
" DIRECTOR UPPER SCHOOL ",
" DIRECTOR LOWER SCHOOL ",
" DIRECTOR MIDDLE SCHOOL ",
" INTERIM HEAD SCHOOL "
)
CEO.Prob.Other <- " MANAGING ATTORNEY "


```

## CFO

```{r CFO}
CFO <- c( " CFO ", 
" CHIEF FINANCIAL OFFICER ", 
" DIRECTOR FINANCE ", 
" FINANCE DIRECTOR ", 
" VICE PRESIDENT FINANCE ", 
" VICE PRESIDENT CFO ", 
" SENIOR VICE PRESIDENT CFO ", 
" CFO TREASURER ", 
" CFO ", 
" CHIEF FINANCIAL OFFICER ", 
" DIRECTOR FINANCE ", 
" FINANCE DIRECTOR ", 
" VICE PRESIDENT FINANCE ", 
" VICE PRESIDENT CFO ", 
" SENIOR VICE PRESIDENT CFO ", 
" CFO TREASURER ", 
" EXECUTIVE VICE PRESIDENT CFO ", 
" TREASURER CFO ", 
" FINANCE MANAGER ", 
" VICE PRESIDENT FINANCE CFO ", 
" FISCAL DIRECTOR ", 
" VICE PRESIDENT FINANCE ADMINISTRATION ", 
" DIRECTOR FINANCE ADMINISTRATION ", 
" FORMER CFO ", 
" FISCAL OFFICER ", 
" FINANCIAL DIRECTOR ", 
" COMPTROLLER ", 
" CFO COO ", 
" DIRECTOR FINANCE OPERATIONS ", 
" ACCOUNTANT ", 
" VICE PRESIDENT FINANCE CFO ", 
" COO CFO ", 
" DIRECTOR FINANCE ", 
" BOOKKEEPER ", 
" DIRECTOR FINANCEOPERATIONS ", 
" VICE PRESIDENT FINANCE ADMINISTRATION ", 
" FINANCE OFFICER ", 
" SENIOR VICE PRESIDENT FINANCE CFO ", 
" SENIOR VICE PRESIDENT FINANCE ", 
" CHIEF FINANCE ", 
" VICE PRESIDENT CHIEF FINANCIAL OFFICER ", 
" FINANCIAL MANAGER ", 
" INTERIM CFO ", 
" VICE PRESIDENT FINANCE ", 
" VICE PRESIDENTCFO ", 
" FISCAL MANAGER ", 
" DIRECTOR FINANCEADMINISTRATION ", 
" DIRECTOR ACCOUNTING ", 
" FINANCIAL OFFICER ", 
" ACCOUNTING MANAGER ", 
" ASSISTANT TREASURER CFO ", 
" FINANCE OFFICER ", 
" CFO ASSISTANT TREASURER ", 
" VICE PRESIDENT FINANCE OPERATIONS ", 
" VICE PRESIDENT FINANCE TREASURER ", 
" CORPORATE CONTROLLER ", 
" DIRECTOR FINANCE ADMINISTRATION ", 
" SENIOR VICE PRESIDENT CHIEF FINANCIAL OFFICER ", 
" VICE PRESIDENT FINANCEADMINISTRATION ", 
" VICE PRESIDENT BUSINESS FINANCE ", 
" CFO VICE PRESIDENT FINANCE ", 
" VICE PRESIDENT FINANCIAL SERVICES ", 
" CHIEF FINANCE OFFICER ", 
" CHIEF FISCAL OFFICER ", 
" SENIOR VICE PRESIDENT CFO TREASURER ", 
" SECRETARY TREASURER CFO ", 
" VICE PRESIDENT REVENUE CYCLE ", 
" VICE PRESIDENT FINANCE ADMINISTRATION ", 
" CFO THRU ", 
" CFO VICE PRESIDENT FINANCE ", 
" SENIOR VICE PRESIDENTCFO ", 
" FORMER CHIEF FINANCIAL OFFICER ", 
" CFO THROUGH ", 
" SENIOR DIRECTOR FINANCE ", 
" TREASURERCFO ", 
" CFO VICE PRESIDENT ", 
" VICE PRESIDENT FINANCEADMINISTRATION ", 
" CEO CFO ", 
" SENIOR VICE PRESIDENT FINANCE ADMINISTRATION ", 
" DIRECTOR FINANCE OPERATIONS ", 
" VICE PRESIDENT CFO TREASURER ", 
" FINANCE MANAGEMENT ", 
" EXECUTIVE VICE PRESIDENTCFO ", 
" TREASURER CF ", 
" CFO UNTIL ", 
" CFO SENIOR VICE PRESIDENT ", 
" DIRECTOR FINANCE HUMAN RESOURCES ", 
" DIRECTOR ADMINISTRATION FINANCE ", 
" EXECUTIVE VICE PRESIDENT FINANCE CFO ", 
" SENIOR VICE PRESIDENT FINANCE CFO ", 
" ACCOUNTING DIRECTOR ", 
" SECRETARY CFO ", 
" TREASURER VICE PRESIDENT FINANCE ", 
" VICE PRESIDENT FINANCE OPERATIONS ", 
" CFO FORMER ", 
" EXECUTIVE VICE PRESIDENT CFO TREASURER ", 
" EXECUTIVE DIRECTOR CFO ", 
" FINANCIAL ", 
" DIRECTOR BUSINESS FINANCE ", 
" FISCAL MANAGEMENT ", 
" TREASURER SENIOR VICE PRESIDENT CFO ", 
" CFO SECRETARY ", 
" FORMER DIRECTOR FINANCE ", 
" SENIOR ACCOUNTANT ", 
" EXECUTIVE VICE PRESIDENT CHIEF FINANCIAL OFFICER ", 
" ASSISTANT VICE PRESIDENT FINANCE ", 
" CONTROLLER CFO ", 
" CFO CONTROLLER ", 
" CFOTREASURER ", 
" CFO PART YEAR ", 
" CFO SECRETARY TREASURER ", 
" CHIEF FINANCIAL OFFICER TREASURER ", 
" VICE PRESIDENT BUSINESS FINANCE ", 
" PRESIDENT CFO ", 
" SENIOR VICE PRESIDENT FINANCE ",
" DIRECTOR ACCOUNTING "
 )

CFO <- unique(CFO)

```

## CFO Problems

```{r CFO Problems}
CFO.Prob <- c(" SENIOR VICE PRESIDENT FINANCE ADMINISTRATION ", " TREASURER CF ")

CFO.Prob <- unique(CFO.Prob)
```

## Treasurer

```{r Treasurer}

Treasurer <- c( 
" TREASURER ", 
" SECRETARY TREASURER ", 
" ASSISTANT SECRETARY TREASURER ", 
" ASSISTANT TREASURER ", 
" CFO TREASURER ", 
" TREASURER ", 
" PRESIDENT TREASURER ", 
" SECRETARY TREASURER ", 
" ASSISTANT SECRETARY TREASURER ", 
" ASSISTANT TREASURER ", 
" CFO TREASURER ", 
" TREASURER CFO ", 
" VICE PRESIDENT TREASURER ", 
" TREASURER SECRETARY ", 
" EXECUTIVE DIRECTOR TREASURER ", 
" ASSISTANT TREASURER CFO ", 
" CFO ASSISTANT TREASURER ", 
" TREASURER DIRECTOR ", 
" VICE PRESIDENT FINANCE TREASURER ", 
" ASSISTANT SECRETARY ASSISTANT TREASURER ", 
" FORMER ASSISTANT SECRETARY TREASURER ", 
" SENIOR VICE PRESIDENT CFO TREASURER ", 
" SECRETARY TREASURER CFO ", 
" SENIOR VICE PRESIDENT TREASURER ", 
" DIRECTOR TREASURER ", 
" SECRETARY TREASURER DIRECTOR ", 
" TREASURERCFO ", 
" VICE PRESIDENT CFO TREASURER ", 
" EXECUTIVE DIRECTOR SECRETARY TREASURER ", 
" TREASURER CF ", 
" EXECUTIVE VICE PRESIDENT TREASURER ", 
" TREASURER EXECUTIVE DIRECTOR ", 
" PRESIDENTTREASURER ", 
" PRESIDENT TREASURER DIRECTOR ", 
" TREASURER VICE PRESIDENT FINANCE ", 
" EXECUTIVE VICE PRESIDENT CFO TREASURER ", 
" TREASURER SENIOR VICE PRESIDENT CFO ", 
" TREASURER TEACHER ", 
" CONTROLLER ASSISTANT TREASURER ", 
" CFOTREASURER ", 
" CFO SECRETARY TREASURER ", 
" CHIEF FINANCIAL OFFICER TREASURER ", 
" SECY TREASURER " )

Treasurer <- Treasurer %>% unique

```

## Treasurer Problems

```{r Treasurer Problems}
Treasurer.Prob <- c(" TREASURER TEACHER " )

Treasurer.Prob <- Treasurer.Prob %>% unique
```

## Deputy CEO

```{r Deputry CEO}

DEP.CEO <- c(
" DEPUTY DIRECTOR ", 
" ASSOCIATE EXECUTIVE DIRECTOR ", 
" ASSISTANT EXECUTIVE DIRECTOR ", 
" ASSISTANT EXECUTIVE DIRECTOR ", 
" DEPUTY DIRECTOR ", 
" ASSOCIATE EXECUTIVE DIRECTOR ", 
" ASSISTANT EXECUTIVE DIRECTOR ", 
" DEPUTY EXECUTIVE DIRECTOR ", 
" ASSISTANT HEAD SCHOOL ", 
" ASSOCIATE HEAD SCHOOL ", 
" ASSISTANT HEADMASTER ", 
" DEPUTY CEO ", 
" ASSISTANT CHIEF ", 
" DEPUTY EXECUTIVE ", 
" CFO SECRETARY TREASURER ", 
" EXECUTIVE VICE PRESIDENT PROVOST ") 

DEP.CEO <- DEP.CEO %>% unique


```


## Deputy CEO Problems

```{r Deputy CEO Problems}
DEP.CEO.Prob <- c( " ASSISTANT CHIEF ", " DEPUTY EXECUTIVE " )

DEP.CEO.Prob <- DEP.CEO.Prob %>% unique

```


## Secretary 

```{r Secretary}
SEC <- c( 
" SECRETARY ", 
" ASSISTANT SECRETARY ", 
" SECRETARY TREASURER ", 
" ASSISTANT SECRETARY TREASURER ", 
" SECRETARY ", 
" ASSISTANT SECRETARY ", 
" SECRETARY TREASURER ", 
" ASSISTANT SECRETARY TREASURER ", 
" EXECUTIVE DIRECTOR SECRETARY ", 
" SECRETARY EXECUTIVE DIRECTOR ", 
" CORPORATE SECRETARY ", 
" VICE PRESIDENT SECRETARY ", 
" SECRETARY DIRECTOR ", 
" PRESIDENT SECRETARY ", 
" EXECUTIVE SECRETARY ", 
" TREASURER SECRETARY ", 
" BOARD SECRETARY ", 
" CEO SECRETARY ", 
" DIRECTOR SECRETARY ", 
" ASSISTANT SECRETARY ASSISTANT TREASURER ", 
" GENERAL COUNSEL SECRETARY ", 
" FORMER ASSISTANT SECRETARY TREASURER ", 
" SECRETARY TREASURER CFO ", 
" SECRETARY GENERAL COUNSEL ", 
" SECRETARY TEACHER ", 
" SCOUT EXECUTIVE SECRETARY ", 
" SECRETARY TREASURER DIRECTOR ", 
" PRESIDENT CEO SECRETARY ", 
" SECRETARY CEO ", 
" VICE PRESIDENT ASSISTANT SECRETARY ", 
" EXECUTIVE DIRECTOR SECRETARY TREASURER ", 
" SECRETARY COO ", 
" COO SECRETARY ", 
" SECRETARY CFO ", 
" CORP SECRETARY ", 
" SECRETARY VICE PRESIDENT ", 
" CFO SECRETARY ", 
" SECY TREASURER ", 
" RECORDING SECRETARY ", 
" SENIOR VICE PRESIDENT SECRETARY ")

SEC <- SEC %>% unique
```

## Secretary Problems

```{r Secretary Problems}
SEC.Prob <- c( " SENIOR VICE PRESIDENT SECRETARY ")


```

## COO

```{r COO}
COO <- c( " COO ", 
" CHIEF OPERATING OFFICER ", 
" MANAGING DIRECTOR ", 
" DIRECTOR OPERATIONS ", 
" VICE PRESIDENT OPERATIONS ", 
" PROVOST ", 
" EXECUTIVE VICE PRESIDENT COO ", 
" VICE PRESIDENT OPERATIONS ", 
" CMO ", 
" VICE PRESIDENT COO ", 
" CHIEF OPERATIONS OFFICER ", 
" INTERIM PROVOST ", 
" COO ", 
" CHIEF OPERATING OFFICER ", 
" MANAGING DIRECTOR ", 
" DIRECTOR OPERATIONS ", 
" VICE PRESIDENT OPERATIONS ", 
" PROVOST ", 
" EXECUTIVE VICE PRESIDENT COO ", 
" VICE PRESIDENT OPERATIONS ", 
" CMO ", 
" VICE PRESIDENT COO ", 
" CHIEF OPERATIONS OFFICER ", 
" CHIEF STAFF ", 
" OPERATIONS DIRECTOR ", 
" VICE PRESIDENT FINANCE ADMINISTRATION ", 
" DIRECTOR FINANCE ADMINISTRATION ", 
" SENIOR VICE PRESIDENT COO ", 
" CHIEF OPERATIONS ", 
" CFO COO ", 
" ADMINISTRATIVE DIRECTOR ", 
" SENIOR VICE PRESIDENT OPERATIONS ", 
" ADMINISTRATION DIRECTOR ", 
" DIRECTOR ADMINISTRATION ", 
" OPERATIONS MANAGER ", 
" ADMINISTRATION ", 
" COO CFO ", 
" DIRECTOR OPERATIONS ", 
" DIRECTOR FINANCEOPERATIONS ", 
" CHIEF ADMINISTRATION OFFICER ", 
" PRESIDENT COO ", 
" VICE PRESIDENT ADMINISTRATION ", 
" VICE PRESIDENT FINANCE ADMINISTRATION ", 
" CHIEF OPERATIONS ", 
" SENIOR VICE PRESIDENT OPERATIONS ", 
" SENIOR VICE PRESIDENT CMO ", 
" DIRECTOR FINANCEADMINISTRATION ", 
" VICE PRESIDENT CMO ", 
" VICE PRESIDENT CLINICAL OPERATIONS ", 
" VICE PRESIDENT FINANCEADMINISTRATION ", 
" VICE PRESIDENT ADMINISTRATION FINANCE ", 
" VICE PRESIDENT FINANCEADMINISTRATION ", 
" DIRECTOR FINANCE ADMINISTRATION ", 
" VICE PRESIDENT CONTROLLER ", 
" EXECUTIVE VICE PRESIDENT CHIEF OPERATING OFFICER ", 
" EXECUTIVE VICE PRESIDENTCOO ", 
" DIRECTOR BUSINESS OPERATIONS ", 
" GENERAL MANAGEMENT ", 
" SENIOR VICE PRESIDENT ADMINISTRATION ", 
" OPERATIONS D ", 
" VICE PRESIDENT ADMINISTRATOR ", 
" VICE PRESIDENT FINANCEADMINISTRATION ", 
" SENIOR VICE PRESIDENT FINANCE ADMINISTRATION ", 
" CHIEF ADMINISTRATION ", 
" FORMER COO ", 
" OPERATIONS ", 
" OPERATIONS MGR ", 
" VICE PRESIDENT CHIEF OPERATING OFFICER ", 
" SENIOR VICE PRESIDENTCOO ", 
" EXECUTIVE DIRECTOR COO ", 
" EXECUTIVE DIRECTOR OPERATIONS ", 
" SENIOR VICE PRESIDENT CHIEF OPERATING OFFICER ", 
" EXECUTIVE VICE PRESIDENT OPERATIONS ", 
" VICE PRESIDENT ADMINISTRATION ", 
" ASSISTANT ADMINISTRATION ", 
" MANAGING EDITOR ", 
" VICE PRESIDENTCOO ", 
" DIRECTOR ADMINISTRATION FINANCE ", 
" BUSINESS ADMINISTRATION ", 
" SECRETARY COO ", 
" COO SECRETARY ", 
" EXECUTIVE ADMINISTRATOR ", 
" OPERATIONS M ", 
" DIRECTOR FINANCEAD ", 
" COO VICE PRESIDENT ", 
" EXECUTIVE VICE PRESIDENT CMO ", 
" PRESIDENT ADMINISTRATOR ", 
" EXECUTIVE VICE PRESIDENT OPERATIONS ", 
" SENIOR DIRECTOR OPERATIONS ", 
" CHIEF OPERATIONAL OFFICER ", 
" EXECUTIVE DIRECTOR OPERATIONS ", 
" VICE PRESIDENT HOSPITAL OPERATIONS ", 
" VICE PRESIDENT OPERATIONS ", 
" INTERIM PROVOST ",
" VICE PRESIDENT ADMINISTRATION ",
" CHIEF ADMINISTRATIVE OFFICER ",
" DIRECTOR ADMINISTRATION "


 )

COO <- COO %>% unique

```

## COO Problems

```{r COO Problems}



COO.Prob <- c( 
" PROVOST ", 
" INTERIM PROVOST ", 
" SENIOR VICE PRESIDENT CMO ", 
" SENIOR VICE PRESIDENT FINANCE ADMINISTRATION ", 
" CHIEF ADMINISTRATION ", 
" MANAGING EDITOR ", 
" EXECUTIVE ADMINISTRATOR ", 
" PRESIDENT ADMINISTRATOR ", 
" INTERIM PROVOST ",
" NURSING HOME ADMINISTRATOR "
 )

COO.Prob <- COO.Prob %>% unique

```

## Director/Trustee 

```{r Director/Trustee}

TRUST <- c(
" BOARD MEMBER ", 
" TRUSTEE ", 
" CHAIR ", 
" MEMBER ", 
" BOARD MEMBER ", 
" TRUSTEE ", 
" CHAIR ", 
" MEMBER ", 
" VICE CHAIR ", 
" FOUNDATION DIRECTOR ", 
" PRESIDENT TRUSTEE ", 
" BOARD MEMBER PHYSICIAN ", 
" BOARD MEMBER TEACHER ", 
" COMMISSIONER ", 
" MEMBER TEACHER ", 
" TRUSTEE PRESIDENT CEO ", 
" SENIOR FELLOW ", 
" PHYSICIAN BOARD MEMBER ", 
" TRUSTEE PHYSICIAN ", 
" FOUNDER ", 
" TRUSTEE PRESIDENT ", 
" PRESIDENT CHAIR ", 
" CHIEF PARTY ", 
" CHAIR PRESIDENT ", 
" PRESIDENT CEO TRUSTEE ", 
" PARTNER ", 
" TRUSTEE TEACHER ", 
" BOARD CHAIR ", 
" FACULTY TRUSTEE ", 
" PRESIDENT BOARD MEMBER ", 
" BOARD MEMBER EXECUTIVE DIRECTOR ", 
" FOUNDING DIRECTOR ", 
" BOARD MEMBER CEO ", 
" BOARD MEMBERDEPT CHAIR ", 
" TEACHER BOARD MEMBER ", 
" TRUSTEE FACULTY ", 
" PHYSICIAN TRUSTEE ", 
" BOARD DIRECTOR ", 
" FACULTY REPRESENTATIVE ", 
" CHAIR DIRECTOR ", 
" EXECUTIVE DIRECTOR BOARD MEMBER ", 
" CO FOUNDER ", 
" CHAIR THE BOARD ", 
" CEO CHAIR ", 
" FOUNDER DIRECTOR ", 
" EXECUTIVE DIRECTOR TRUSTEE ", 
" TRUSTEE EXECUTIVE DIRECTOR ", 
" VICE CHAIR CEO ", 
" CEO TRUSTEE ", 
" PRESIDENTTRUSTEE ", 
" BOARD MEMBER PRESIDENT CEO ", 
" ASSOCIATE COMMISSIONER ", 
" DIRECTOR CHAIR ", 
" MEDICAL STAFF PRESIDENT ", 
" BOARD MEMBER PRESIDENT ", 
" BOARD PRESIDENT ", 
" EX OFFICER MEMBER ", 
" PRESIDENT CEO BOARD MEMBER ", 
" STAFF REPRESENTATIVE ",
" CHIEF STAFF "
)

TRUST <- TRUST %>% unique

```


## Director/Trustee Problems

```{r Director/Trustee Problems}
TRUST.Prob <- c( 
" CHAIR ", 
" MEMBER ", 
" CHAIR ", 
" MEMBER ", 
" VICE CHAIR ", 
" FOUNDATION DIRECTOR ", 
" PRESIDENT TRUSTEE ", 
" COMMISSIONER ", 
" MEMBER TEACHER ", 
" TRUSTEE PRESIDENT CEO ", 
" SENIOR FELLOW ", 
" FOUNDER ", 
" TRUSTEE PRESIDENT ", 
" PRESIDENT CHAIR ", 
" CHIEF PARTY ", 
" CHAIR PRESIDENT ", 
" PRESIDENT CEO TRUSTEE ", 
" PARTNER ", 
" BOARD CHAIR ", 
" PRESIDENT BOARD MEMBER ", 
" BOARD MEMBER EXECUTIVE DIRECTOR ", 
" FOUNDING DIRECTOR ", 
" BOARD MEMBER CEO ", 
" BOARD MEMBERDEPT CHAIR ", 
" BOARD DIRECTOR ", 
" FACULTY REPRESENTATIVE ", 
" CHAIR DIRECTOR ", 
" EXECUTIVE DIRECTOR BOARD MEMBER ", 
" CO FOUNDER ", 
" CHAIR THE BOARD ", 
" CEO CHAIR ", 
" FOUNDER DIRECTOR ", 
" EXECUTIVE DIRECTOR TRUSTEE ", 
" TRUSTEE EXECUTIVE DIRECTOR ", 
" VICE CHAIR CEO ", 
" CEO TRUSTEE ", 
" PRESIDENTTRUSTEE ", 
" BOARD MEMBER PRESIDENT CEO ", 
" ASSOCIATE COMMISSIONER ", 
" DIRECTOR CHAIR ", 
" MEDICAL STAFF PRESIDENT ", 
" BOARD MEMBER PRESIDENT ", 
" BOARD PRESIDENT ", 
" EX OFFICER MEMBER ", 
" PRESIDENT CEO BOARD MEMBER ", 
" STAFF REPRESENTATIVE " )

TRUST.Prob <- TRUST.Prob %>% unique


TRUST.Prob.CEO <- c(
" CHAIR ",
" FOUNDATION DIRECTOR ",
" PRESIDENT TRUSTEE ",
" COMMISSIONER ",
" TRUSTEE PRESIDENT CEO ",
" FOUNDER ",
" TRUSTEE PRESIDENT ",
" PRESIDENT CHAIR ",
" CHIEF PARTY ",
" CHAIR PRESIDENT ",
" PRESIDENT CEO TRUSTEE ",
" BOARD CHAIR ",
" PRESIDENT BOARD MEMBER ",
" BOARD MEMBER EXECUTIVE DIRECTOR ",
" FOUNDING DIRECTOR ",
" BOARD MEMBER CEO ",
" EXECUTIVE DIRECTOR BOARD MEMBER ",
" CO FOUNDER ",
" CHAIR THE BOARD ",
" CEO CHAIR ",
" FOUNDER DIRECTOR ",
" EXECUTIVE DIRECTOR TRUSTEE ",
" TRUSTEE EXECUTIVE DIRECTOR ",
" VICE CHAIR CEO ",
" CEO TRUSTEE ",
" PRESIDENTTRUSTEE ",
" BOARD MEMBER PRESIDENT CEO ",
" BOARD MEMBER PRESIDENT ",
" BOARD PRESIDENT ",
" PRESIDENT CEO BOARD MEMBER ",
" ASSOCIATE COMMISSIONER "
)


TRUST.Prob.BOARD<- c( 
" MEMBER ",
" MEMBER TEACHER ",
" SENIOR FELLOW ",
" PARTNER ",
" BOARD MEMBERDEPT CHAIR ",
" BOARD DIRECTOR ",
" FACULTY REPRESENTATIVE ",
" CHAIR DIRECTOR ",
" DIRECTOR CHAIR ",
" EX OFFICER MEMBER ",
" STAFF REPRESENTATIVE ")


TRUST.Prob.DEP.CEO <- c(" ASSOCIATE COMMISSIONER " )

TRUST.Prob.MAN <- c( 
" MEDICAL STAFF PRESIDENT ",
" STAFF REPRESENTATIVE ",
" CHAIR "
)

TRUST.Prob.OTHER<- c(
" MEMBER ",
" MEMBER TEACHER ",
" SENIOR FELLOW ",
" PARTNER ",
" EX OFFICER MEMBER ",
" FOUNDATION DIRECTOR ",
" COMMISSIONER ",
" CHIEF PARTY ",
" FOUNDING DIRECTOR ")

```

## Human Resources

```{r Human Resources}
HUM.RES <- c( 
" VICE PRESIDENT HUMAN RESOURCES ", 
" DIRECTOR HUMAN RESOURCES ", 
" VICE PRESIDENT HUMAN RESOURCES ", 
" VICE PRESIDENT HUMAN RESOURCES ", 
" DIRECTOR HUMAN RESOURCES ", 
" VICE PRESIDENT HUMAN RESOURCES ", 
" HUMAN RESOURCES DIRECTOR ", 
" CHIEF HUMAN RESOURCES OFFICER ", 
" SENIOR VICE PRESIDENT HUMAN RESOURCES ", 
" DIRECTOR HUMAN RESOURCES ", 
" HUMAN RESOURCES ", 
" SENIOR VICE PRESIDENT CHIEF HUMAN RESOURCES OFFICER ", 
" VICE PRESIDENT CHIEF HUMAN RESOURCES OFFICER ", 
" VICE PRESIDENT HUMAN RESOURCES ", 
" EXECUTIVE DIRECTOR HUMAN RESOURCES ", 
" SENIOR VICE PRESIDENT HUMAN RESOURCES ", 
" DIRECTOR FINANCE HUMAN RESOURCES ", 
" DIRECTOR STAFF ", 
" ASSISTANT VICE PRESIDENT HUMAN RESOURCES ",
" DIRECTOR EMPLOYEE ",
" VICE PRESIDENT PROFESSIONAL SERVICES ",
" DIRECTOR FINANCE HUMAN RESOURCES "
)

HUM.RES <- HUM.RES %>% unique

```

## Human Resources Problems

```{r Human Resources Problems}

HUM.RES.Prob <- c( " DIRECTOR STAFF " )

```

## Communications

```{r Communications}

COMM <- c( 
" DIRECTOR MARKETING ", 
" VICE PRESIDENT MARKETING ", 
" CHIEF MARKETING OFFICER ", 
" MARKETING DIRECTOR ", 
" DIRECTOR COMMUNICATIONS ", 
" VICE PRESIDENT COMMUNICATIONS ", 
" VICE PRESIDENT MARKETING ", 
" VICE PRESIDENT EXTERNAL AFFAIRS ", 
" COMMUNICATIONS DIRECTOR ", 
" VICE PRESIDENT MARKETING COMMUNICATIONS ", 
" VICE PRESIDENT COMMUNICATIONS ", 
" VICE PRESIDENT MARKETING COMMUNICATIONS ", 
" SENIOR VICE PRESIDENT MARKETING ", 
" DIRECTOR EXTERNAL AFFAIRS ", 
" DIRECTOR COMMUNICATIONS ", 
" CHIEF COMMUNICATIONS OFFICER ", 
" DIRECTOR COMMUNICATIONS ", 
" VICE PRESIDENT MARKETING DEVELOPMENT ", 
" DIRECTOR MARKETING ", 
" VICE PRESIDENT GOVERNMENT RELATIONS ", 
" VICE PRESIDENT EXTERNAL RELATIONS ", 
" VICE PRESIDENT UNIVERSITY RELATIONS ", 
" DIRECTOR PUBLICATIONS ", 
" VICE PRESIDENT PUBLIC RELATIONS ", 
" VICE PRESIDENT COMMUNICATIONS ", 
" VICE PRESIDENT PUBLIC AFFAIRS ", 
" VICE PRESIDENT COMMUNICATIONS MARKETING ", 
" VICE PRESIDENT COMMUNICATIONS ", 
" DIRECTOR PUBLICATIONS ",
" VICE PRESIDENT GOVERNMENT AFFAIRS ",
" DIRECTOR INVESTMENTS ",
" DIRECTOR PLANNED GIVING ",
" ARTISTIC DIRECTOR ",
" ARTISTIC DIRECTOR ",
" EXECUTIVE ARTISTIC DIRECTOR ",
" PRODUCING ARTISTIC DIRECTOR ",
" ASSOCIATE ARTISTIC DIRECTOR ",
" CO ARTISTIC DIRECTOR ",
" PRESIDENT ARTISTIC DIRECTOR ",
" PROGRAM DIRECTOR ",
" ASSISTANT VICE PRESIDENT ",
" VICE PRESIDENT MARKETING DEVELOPMENT "
)

COMM <- COMM %>% unique

```

## Management 

```{r Management}

MAN <- c(
" DIRECTOR ",
" VICE PRESIDENT ",
" ADMINISTRATOR ",
" CONTROLLER ",
" EXECUTIVE VICE PRESIDENT ",
" SENIOR VICE PRESIDENT ",
" ASSISTANT DIRECTOR ",
" ASSOCIATE DIRECTOR ",
" MANAGER ",
" DIRECTOR ",
" OFFICER ",
" CO DIRECTOR ",
" GENERAL MANAGER ",
" DIRECTOR ",
" VICE PRESIDENT ",
" ADMINISTRATOR ",
" CONTROLLER ",
" EXECUTIVE VICE PRESIDENT ",
" SENIOR VICE PRESIDENT ",
" ASSISTANT DIRECTOR ",
" ASSOCIATE DIRECTOR ",
" MANAGER ",
" DIRECTOR ",
" OFFICER ",
" CO DIRECTOR ",
" GENERAL MANAGER ",
" FORMER OFFICER ",
" SENIOR DIRECTOR ",
" REGIONAL DIRECTOR ",
" VICE PRESIDENT DIRECTOR ",
" EX DIRECTOR ",
" COORDINATOR ",
" EX OFFICER ",
" FORMER DIRECTOR ",
" FORMER DIRECTOR ",
" DIVISION DIRECTOR ",
" DIRECTOR TEACHER ",
" ASSOCIATE VICE PRESIDENT ",
" GENERAL DIRECTOR ",
" SUPERVISOR ",
" FORMER VICE PRESIDENT ",
" EDITOR ",
" DEPARTMENT DIRECTOR ",
" DIRECTOR VICE PRESIDENT ",
" NATIONAL DIRECTOR ",
" SITE DIRECTOR ",
" STATE DIRECTOR ",
" STORE MANAGER ",
" UNIT DIRECTOR ",
" OFFICER MGR ",
" COUNTRY DIRECTOR ",
" VICE PRINCIPAL ",
" DISTRICT VICE PRESIDENT ",
" BRANCH DIRECTOR ",
" ASSIST DIRECTOR ",
" DIVISIONAL DIRECTOR ",
" GROUP VICE PRESIDENT ",
" DIVISION CHIEF ",
" FORMER EXECUTIVE VICE PRESIDENT ",
" REGIONAL VICE PRESIDENT ",
" DIRECTOR FOUNDATION ",
" FORMER DIRECTOR ",
" FORMER VICE PRESIDENT ",
" KEY EMPLOYEE ",
" FORMER KEY EMPLOYEE "
)

MAN <- MAN %>% unique
```

## Management Problems

```{r Management Problems}

MAN.Prob <- c( 
" DEAN ", 
" DEAN ", 
" OFFICER ", 
" FORMER OFFICER ", 
" CAO ", 
" EX DIRECTOR ", 
" EX OFFICER ", 
" FORMER DIRECTOR ", 
" BUSINESS MGR ", 
" ASSOCIATE DEAN ", 
" CENTER DIRECTOR ", 
" BUSINESS MANAGEMENT ", 
" ASSISTANT PRINCIPAL ", 
" HEAD LOWER SCHOOL ", 
" GENERAL DIRECTOR ", 
" EDITOR ", 
" RESEARCH DIRECTOR ", 
" BOARD MEMBERDEPT CHAIR ", 
" REGIONAL EXECUTIVE DIRECTOR ", 
" COUNTRY DIRECTOR ", 
" HEAD COACH MEN S BASKETBALL ", 
" HEAD BASKETBALL COACH ", 
" MEN S BASKETBALL COACH " 
 )

MAN.Prob <- MAN.Prob %>% unique
```

## Technology

```{r Technology}

TECH <- c( 
" CHIEF INFOMATION OFFICER ", 
" DIRECTOR IT ", 
" IT DIRECTOR ", 
" VICE PRESIDENT CIO ", 
" DIRECTOR TECHNOLOGY ", 
" CHIEF TECHNOLOGY OFFICER ", 
" CDO ", 
" CIO ", 
" VICE PRESIDENT INFOMATION TECHNOLOGY ", 
" VICE PRESIDENT CHIEF INFOMATION OFFICER ", 
" SENIOR VICE PRESIDENT CIO ", 
" DIRECTOR INFOMATION TECHNOLOGY ", 
" DIRECTOR IT ", 
" CTO ", 
" IT MANAGER ", 
" VICE PRESIDENT INFOMATION SERVICES ", 
" VICE PRESIDENT INFOMATION SYSTEMS ", 
" CHIEF INFOMATION OFFICER ", 
" SENIOR VICE PRESIDENT CHIEF INFOMATION OFFICER ", 
" VICE PRESIDENT IT ", 
" DIRECTOR INFOMATION SYSTEMS ", 
" DIRECTOR INFOMATION TECHNOLOGY ", 
" DIRECTOR MANAGEMENT INFOMATION SYSTEMS ", 
" CHIEF MEDICAL INFOMATION OFFICER ", 
" VICE PRESIDENT INFOMATION TECHNOLOGY ", 
" VICE PRESIDENT TECHNOLOGY ", 
" DIRECTOR INFOMATION SYSTEMS ", 
" CHIEF INNOVATION OFFICER " ) 

TECH <- TECH %>% unique
```


## Development

```{r Development}

DEV <- c(
" DIRECTOR DEVELOPMENT ", 
" VICE PRESIDENT DEVELOPMENT ", 
" CHIEF DEVELOPMENT OFFICER ", 
" CHIEF DEVELOPMENT OFFICER ", 
" VICE PRESIDENT DEVELOPMENT ", 
" DIRECTOR DEVELOPMENT ", 
" VICE PRESIDENT DEVELOPMENT ", 
" CHIEF DEVELOPMENT OFFICER ", 
" CHIEF DEVELOPMENT OFFICER ", 
" VICE PRESIDENT DEVELOPMENT ", 
" VICE PRESIDENT BUSINESS DEVELOPMENT ", 
" SENIOR VICE PRESIDENT DEVELOPMENT ", 
" DIRECTOR DEVELOPMENT ", 
" VICE PRESIDENT DEVELOPMENT ", 
" DEVELOPMENT ", 
" VICE PRESIDENT INSTITUTIONAL ADVANCEMENT ", 
" DIRECTOR BUSINESS DEVELOPMENT ", 
" SENIOR DIRECTOR DEVELOPMENT ", 
" SENIOR VICE PRESIDENT BUSINESS DEVELOPMENT ", 
" DIRECTOR BUSINESS DEVELOPMENT ", 
" VICE PRESIDENT PHILANTHROPY ", 
" VICE PRESIDENT BUSINESS DEVELOPMENT ", 
" VICE PRESIDENT INSTITUTION ADVANCEMENT ", 
" DIRECTOR MAJOR GIFTS ", 
" VICE PRESIDENT FUND DEVELOPMENT ", 
" VICE PRESIDENT UNIVERSITY ADVANCEMENT ", 
" DEVELOPMENT OFFICER ", 
" DIRECTOR INSTITUTIONAL ADVANCEMENT ", 
" VICE PRESIDENT PHILANTHROPY ", 
" DO ", 
" VICE PRESIDENT RESOURCES DEVELOPMENT ", 
" VICE PRESIDENT CHIEF DEVELOPMENT OFFICER ", 
" EXECUTIVE DIRECTOR DEVELOPMENT ", 
" DIRECTOR PLANNED GIVING ", 
" SENIOR VICE PRESIDENT ADVANCEMENT ", 
" SENIOR DIRECTOR DEVELOPMENT ", 
" ASSISTANT VICE PRESIDENT DEVELOPMENT ", 
" CHIEF PHILANTHROPY OFFICER ", 
" SENIOR VICE PRESIDENT DEVELOPMENT ",
" DEVELOPMENT DIRECTOR ",
" VICE PRESIDENT INSTITUTIONAL ADVANCEMENT ",
" VICE PRESIDENT ADVANCEMENT ",
" DIRECTOR ADVANCEMENT ",
" CHIEF INVESTMENT OFFICER ",
" VICE PRESIDENT ADVANCEMENT ",
" CHIEF ADVANCEMENT OFFICER ",
" VICE PRESIDENT MARKETING DEVELOPMENT "
 ) 

DEV <- DEV %>% unique
```

## Development Problems

```{r Development Problems}

DEV.Prob <- c( " DO ") 


```

## OTHER Revision

```{r}
OTHER <- c(
    " EMPLOYEE ",
" STAFF ",
" CLERK ",
" HIGHEST COMPENSATED EMPLOYEE ",
" COACH ",
" INVESTIGATOR ",
" PRINCIPAL INVESTIGATOR ",
" ASSOCIATE ",
" HIGHEST COMPENSATED EMPLOY ",
" STAGEHAND ",
" SEE SCHEDULE O ",
" SEE SCHEDULE O O T TITLES "
)

OTHER <- OTHER %>% unique()
```

## Project Mangement

```{r}
PROJECT <-c(
" CHIEF PROGRAM OFFICER ",
" SENIOR VICE PRESIDENT PROGRAM ",
" DIRECTOR PROGRAM OPERATIONS ",
" VICE PRESIDENT PROGRAMMING ",
" DIRECTOR PROGRAM SERVICES ",
" PROGRAM DIRECTOR ",
" PROGRAM MANAGER ",
" PROJECT DIRECTOR ",
" VICE PRESIDENT PROGRAM ",
" DIRECTOR PROGRAM ",
" VICE PRESIDENT PROGRAM ",
" PROJECT MANAGER ",
" PROGRAM COORDINATOR ",
" SENIOR PROGRAM DIRECTOR ",
" PROGRAM OFFICER ",
" DIRECTOR PROGRAM ",
" SENIOR PROGRAM MANAGER ",
" SENIOR PROJECT MANAGER ",
" PROGRAM ADMINISTRATOR ",
" PROJECT COORDINATOR ",
" ASSISTANT PROGRAM DIRECTOR ",
" ASSISTANT PROGRAM DIRECTOR ",
" VICE PRESIDENT PROGRAM SERVICES ",
" DIRECTOR SPECIAL PROJECT ",
" DIRECTOR PROGRAMMING "
)

PROJECT <- PROJECT %>% unique()
```

## LEGAL

```{r}
LEGAL <- c(
" SENIOR VICE PRESIDENT GENERAL COUNSEL ",
" CHIEF COMPLIANCE OFFICER ",
" CCO ",
" CHIEF LEGAL OFFICER ",
" LEGAL DIRECTOR ",
" COMPLIANCE OFFICER ",
" VICE PRESIDENT GENERAL COUNSEL ",
" EXECUTIVE VICE PRESIDENT GENERAL COUNSEL ",
" VICE PRESIDENT PUBLIC POLICY ",
" POLICY DIRECTOR ",
" DIRECTOR LITIGATION ",
" VICE PRESIDENT COMPLIANCE ",
" VICE PRESIDENT POLICY ",
" DIRECTOR PUBLIC POLICY ",
" DIRECTOR COMPLIANCE ",
" VICE PRESIDENT GENERAL COUNSEL ",
" VICE PRESIDENT LEGAL AFFAIRS ",
" VICE PRESIDENT GENERAL COUNSEL SECRETARY ",
" DEPUTY GENERAL COUNSEL ",
" GENERAL COUNSEL ",
" SUPERVISING ATTORNEY ",
" ATTORNEY ",
" SENIOR ATTORNEY ",
" COUNSELOR ",
" CHIEF COUNSEL ",
" LEGAL COUNSEL ",
" MEMBER COUNSEL ",
" ASSOCIATE GENERAL COUNSEL ",
" SENIOR COUNSEL ",
" ASSOCIATE GENERAL COUNSEL "
)

LEGAL <- LEGAL %>% unique()
```


## FACILITIES

```{r}
FACILITIES <- c(
" DIRECTOR FACILITIES ",
" VICE PRESIDENT FACILITIES ",
" FACILITIES DIRECTOR ",
" VICE PRESIDENT FACILITIES MANAGEMENT ",
" FACILITY DIRECTOR ",
" MAINTENANCE "
)

FACILITIES <- FACILITIES %>% unique()
```

## Administrative Support

```{r}
ADMIN.SUP <- c(
" VICE PRESIDENT SUPPORT SERVICES ",
" VICE PRESIDENT ANCILLARY SERVICES ",
" VICE PRESIDENT ADMINISTRATIVE SERVICES ",
" DIRECTOR SUPPORT SERVICES ",
" ASSISTANT ADMINISTRATOR ",
" OFFICER ADMINISTRATION ",
" ASSISTANT SE ",
" EXECUTIVE ASSISTANT ",
" ADMINISTRATION ASSISTANT ",
" ADMINISTRATIVE ASSISTANT ",
" OFFICER MANAGEMENT "
)

ADMIN.SUP <- ADMIN.SUP %>% unique()
```

## Health and Medical

```{r}
MED.MAN <- c(
" VICE PRESIDENT CNE ", 
" MEDICAL DIRECTOR ",
" CHIEF MEDICAL OFFICER ",
" DIRECTOR NURSING ",
" CHIEF NURSING OFFICER ",
" CNO ",
" VICE PRESIDENT MEDICAL AFFAIRS ",
" DIRECTOR PHARMACY ",
" PHARMACY DIRECTOR ",
" ASSOCIATE MEDICAL DIRECTOR ",
" DIRECTOR PHARMACY ",
" VICE PRESIDENT PATIENT CARE SERVICES ",
" PHARMACY MANAGER ",
" VICE PRESIDENT CLINICAL SERVICES ",
" CHIEF CLINICAL OFFICER ",
" MED DIRECTOR ",
" VICE PRESIDENT PATIENT CARE ",
" VICE PRESIDENT CHIEF NURSING OFFICER ",
" ASSISTANT MEDICAL DIRECTOR ",
" CLINIC DIRECTOR ",
" SENIOR VICE PRESIDENT MEDICAL AFFAIRS ",
" VICE PRESIDENT PATIENT SERVICES ",
" SENIOR VICE PRESIDENT CHIEF NURSING OFFICER ",
" VICE PRESIDENT NURSING ",
" NURSING SUPERVISOR ",
" PHYSICIAN DIRECTOR ",
" NURSE MANAGER ",
" NURSING DIRECTOR ",
" DIRECTOR NURSING ",
" VICE PRESIDENT MEDICAL AFFAIRS ",
" DIRECTOR CLINICAL SERVICES ",
" SENIOR VICE PRESIDENT CNO ",
" VICE PRESIDENT BUSINESS ",
" CLINICAL MANAGER ",
" SENIOR VICE PRESIDENT CHIEF MEDICAL OFFICER ",
" VICE PRESIDENT CHIEF MEDICAL OFFICER ",
" VICE PRESIDENT MED AFFAIRS ",
" DIRECTOR REHAB ",
" VICE PRESIDENT CLINICAL ",
" CHIEF DENTAL OFFICER ",
" CHIEF MEDICAL DIRECTOR ",
" DIRECTOR HEALTH SERVICES ",
" ASSISTANT DIRECTOR NURSING ",
" PHYSICIAN MEDICAL DIRECTOR ",
" VICE PRESIDENT MANAGED CARE ",
" MANAGER PHARMACY ",
" VICE PRESIDENT AMBULATORY SERVICES ",
" VICE PRESIDENT PHYSICIAN SERVICES ",
" VICE PRESIDENT NURSING SERVICES ",
" CLINICAL COORDINATOR ",
" DIRECTOR REHABILITATION ",
" VICE PRESIDENT CLINICAL OPERATIONS ",
" CHIEF NURSE EXECUTIVE ",
" VICE PRESIDENT MEDICAL AFFAIRS CMO ",
" REGIONAL MEDICAL DIRECTOR ",
" VICE PRESIDENT SURGICAL SERVICES ",
" DEAN SCHOOL NURSING ",
" EXECUTIVE MEDICAL DIRECTOR ",
" MDS COORDINATOR ",
" VICE PRESIDENT PATIENT CARE SERVICE ",
" ASSISTANT VICE PRESIDENT NURSING ",
" CHIEF MED OFFICER ",
" DIRECTOR CARE AIDE ",
" SENIOR MEDICAL DIRECTOR ",
" VICE PRESIDENT NURSING ",
" DIRECTOR CLINICAL SERVICES ",
" DIRECTOR HEALTH SERVICES ",
" DIRECTOR REHAB ",
" DIRECTOR CLINICAL SERVICE ",
" NURSING HOME ADMINISTRATOR ",
" VICE PRESIDENT HEALTH SERVICES ",
" DIRECTOR SURGICAL SERVICES ",
" ASSISTANT DIRECTOR NURSING ",
" DIRECTOR PATIENT SERVICES ",
" DEAN SCHOOL NURSING ",
" VICE PRESIDENT MEDICAL SERVICES ",
" DIRECTOR PHARMACY SERVICES ",
" SENIOR VICE PRESIDENT MANAGED CARE ",
" SENIOR VICE PRESIDENT PATIENT CARE SERVICES ",
" DIRECTOR REHAB SERVICES ",
" VICE PRESIDENT PATIENT CARE SERVICES CNO ",
" DIRECTOR DINING SERVICES ",
" VICE PRESIDENT NURSING CNO ",
" CHIEF MEDICAL ",
" VICE PRESIDENT CNE ",
" NURSING HOME ADMINISTRATOR ",
" VICE PRESIDENT CLINICAL OPERATIONS ",
" CLINICAL DIRECTOR ",
" DENTAL DIRECTOR ",
" VICE PRESIDENT CNO ",
" DIRECTOR PHYSICIAN "
)

MED.MAN <- MED.MAN %>% unique()

```


## Health and Human Services

```{r}
HEALTH.HUM <- c(
" SHELTER MANAGER ",
" HOUSING DIRECTOR ",
" SHELTER DIRECTOR ",
" CASE MANAGER "
)

HEALTH.HUM <- HEALTH.HUM %>% unique()
```


## Training and Education


```{r}
TRAIN <- c( 
" DIRECTOR EDUCATION ",
" TRAINING DIRECTOR ",
" EDUCATION DIRECTOR ",
" VICE PRESIDENT EDUCATION ",
" TRAINING COORDINATOR ",
" DIRECTOR TRAINING ",
" VICE PRESIDENT EDUCATION ",
" EDUCATIONAL DIRECTOR ",
" CHIEF LEARNING OFFICER ",
" DIRECTOR INSTRUCTION ",
" DIRECTOR TRAINING ",
" DIRECTOR INSTRUCTION ",
" VICE PRESIDENT CNE "
)

TRAIN <- TRAIN %>% unique()

```

## Academic Management

```{r}
ACADEMIC.MAN <- c( 
    " VICE PRESIDENT ACADEMIC AFFAIRS ",
" VICE PRESIDENT STUDENT AFFAIRS ",
" CHIEF ACADEMIC OFFICER ",
" DEAN FACULTY ",
" VICE PRESIDENT ACADEMIC AFFAIRS ",
" CHIEF ACADEMICS ",
" DEAN SCHOOL BUSINESS ",
" VICE PRESIDENT STUDENT LIFE ",
" VICE PRESIDENT STUDENT DEVELOPMENT ",
" VICE PRESIDENT ACADEMICS ",
" VICE PRESIDENT STUDENT AFFAIRS ",
" VICE PRESIDENT STUDENT LIFE ",
" DEAN SCHOOL EDUCATION ",
" VICE PRESIDENT ACADEMIC ",
" DEAN ADMISSIONS ",
" DIRECTOR COLLEGE COUNSELING ",
" ACADEMIC DIRECTOR ",
" VICE PRESIDENT STUDENT SERVICES ",
" DEAN LAW SCHOOL ",
" VICE PRESIDENT STUDENT DEVELOPMENT ",
" DEAN ACADEMIC AFFAIRS ",
" DEAN COLLEGE BUSINESS ",
" VICE PRESIDENT ACADEMIC AFFAIRS ",
" DEAN STUDENTS ",
" CHIEF ACADEMIC OFFICER ",
" ACADEMIC DEAN ",
" DEAN FACULTY ",
" CHIEF ACADEMICS ",
" DEAN SCHOOL BUSINESS ",
" PROVOST VICE PRESIDENT ACADEMIC AFFAIRS ",
" DIRECTOR COLLEGE COUNSELING ",
" VICE PRESIDENT COLLEGE ADVANCEMENT ",
" DEAN SCHOOL EDUCATION ",
" VICE PRESIDENT ACADEMIC ",
" DEAN ADMISSIONS ",
" ACADEMIC DIRECTOR ",
" DIRECTOR SURGERY ",
" DEAN ACADEMIC AFFAIRS ",
" DEAN COLLEGE BUSINESS ",
" VICE PRESIDENT DEAN ",
" DEAN THE COLLEGE ",
" HEAD UPPER SCHOOL ",
" DEAN LAW SCHOOL ",
" ASSOCIATE PROFESSOR ",
" ASSOCIATE DEAN ",
" ACADEMIC DEAN ",
" ASSOCIATE PROVOST ",
" VICE CHANCELLOR ",
" DEPARTMENT CHAIR ",
" DEAN "
)

ACADEMIC.MAN <- ACADEMIC.MAN %>% unique()
```


## Department Head

```{r}
DEP.HEAD <- c(
" DIRECTOR ADMISSIONS ",
" ATHLETIC DIRECTOR ",
" LIBRARY DIRECTOR ",
" VICE PRESIDENT ENROLLMENT MANAGEMENT ",
" MUSIC DIRECTOR ",
" CHIEF STRATEGY OFFICER ",
" CPO ",
" DIRECTOR RESEARCH ",
" DIRECTOR ATHLETICS ",
" HEAD MIDDLE SCHOOL ",
" VICE PRESIDENT RESEARCH ",
" VICE PRESIDENT ENROLLMENT ",
" DIRECTOR SALES ",
" BUSINESS DIRECTOR ",
" VICE PRESIDENT ENROLLMENT MANAGEMENT ",
" TECHNICAL DIRECTOR ",
" CHIEF PROFESSIONAL OFFICER ",
" VICE PRESIDENT ENROLLMENT ",
" DIRECTOR COACHING ",
" CHIEF QUALITY OFFICER ",
" VICE PRESIDENT QUALITY ",
" EXECUTIVE VICE PRESIDENT CAO ",
" SENIOR VICE PRESIDENT STRATEGY PLANNING ",
" CHIEF CURATOR ",
" DIRECTOR R D ",
" VICE PRESIDENT PROFESSIONAL SERVICES ",
" HEAD FOOTBALL COACH ",
" SENIOR VICE PRESIDENT CAO ",
" HEAD START DIRECTOR ",
" CHIEF SCIENTIFIC OFFICER ",
" VICE PRESIDENT ADMISSIONS ",
" VICE PRESIDENT ENROLLMENT ",
" VICE PRESIDENT STRATEGY PLANNING ",
" CHIEF BUSINESS OFFICER ",
" DIRECTOR INVESTMENTS ",
" VICE PRESIDENT BUSINESS AFFAIRS ",
" SALES MANAGER ",
" SENIOR VICE PRESIDENT PLANNING ",
" LAB DIRECTOR ",
" PRODUCING DIRECTOR ",
" VICE PRESIDENT SALES ",
" SENIOR VICE PRESIDENT MISSION INTEGRATION ",
" EXECUTIVE DIRECTOR LEADERSHIP INSTITUTION ",
" DIRECTOR PRODUCTION ",
" CREATIVE DIRECTOR ",
" VICE PRESIDENT MISSION ",
" DIRECTOR ADMISSION ",
" ADMISSIONS DIRECTOR ",
" VICE PRESIDENT PLANNING ",
" TEACHER DIRECTOR ",
" VICE PRESIDENT ENGINEERING ",
" VICE PRESIDENT MISSION INTEGRATION ",
" CBO ",
" DIRECTOR RESEARCH ",
" SCIENTIFIC DIRECTOR ",
" SENIOR VICE PRESIDENT CHIEF QUALITY OFFICER ",
" DIRECTOR ADMISSIONS ",
" DIRECTOR ADVANCEMENT ",
" DIRECTOR ATHLETICS ",
" DIRECTOR SALES ",
" DIRECTOR FINANCIAL SERVICES ",
" DEAN ARTS SCIENCES ",
" VICE PRESIDENT FINANCIAL AFFAIRS ",
" VICE PRESIDENT STRATEGY ",
" VICE PRESIDENT BUSINESS SERVICES ",
" DIRECTOR ADMISSION ",
" DIRECTOR FINANCIAL SERVICE ",
" DIRECTOR PRODUCTION ",
" DIRECTOR RISK MANAGEMENT ",
" VICE PRESIDENT ENROLLMENT SERVICES ",
" VICE PRESIDENT RISK MANAGEMENT ",
" VICE PRESIDENT RETAIL ",
" DIRECTOR MEMBERSHIP ",
" CHIEF PROFESSIONAL OFFICER ",
" CHIEF CURATOR ",
" HEAD FOOTBALL COACH ",
" EXECUTIVE DIRECTOR LEADERSHIP INSTITUTION ",
" BUSINESS MANAGER ",
" BUSINESS MANAGER ",
" CAO ",
" BUSINESS MGR ",
" CENTER DIRECTOR ",
" BUSINESS MANAGEMENT ",
" ASSISTANT PRINCIPAL ",
" HEAD LOWER SCHOOL ",
" RESEARCH DIRECTOR ",
" VICE PRESIDENT FOUNDATION ",
" VICE PRESIDENT ENROLLMENT MANAGEMENT ",
" BUSINESS ADMINISTRATOR ",
" HEAD COACH MEN S BASKETBALL ",
" HEAD BASKETBALL COACH ",
" MEN S BASKETBALL COACH ",
" BUSINESS OFFICER "
)

DEP.HEAD <- DEP.HEAD %>% unique()
```

## Profesional

```{r}
PROFESIONAL <- c(
" PHYSICIAN ",
" PSYCHIATRIST ",
" PHARMACIST ",
" PROFESSOR ",
" DENTIST ",
" CRNA ",
" DOCTOR ",
" MD ",
" TEACHER ",
" FACULTY ",
" KEY EMPLOYEE ",
" STAFF PHYSICIAN ",
" RN ",
" REGISTERED NURSE ",
" NURSE PRACTITIONER ",
" PHYSICIAN ",
" PSYCHIATRIST ",
" PHARMACIST ",
" PROFESSOR ",
" DENTIST ",
" CRNA ",
" DOCTOR ",
" MD ",
" TEACHER ",
" FACULTY ",
" STAFF PHYSICIAN ",
" RN ",
" REGISTERED NURSE ",
" NURSE PRACTITIONER ",
" SURGEON ",
" PHYSICAL THERAPIST ",
" MEDICAL DOCTOR ",
" PHYSICIAN ASSISTANT ",
" INSTRUCTOR ",
" CARDIOLOGIST ",
" ANESTHESIOLOGIST ",
" PEDIATRICIAN ",
" PROVIDER ",
" ER PHYSICIAN ",
" NURSE ",
" PASTOR ",
" ORTHOPEDIC SURGEON ",
" HOSPITALIST ",
" SENIOR SCIENTIST ",
" OB GYN ",
" RADIOLOGIST ",
" STAFF PSYCHIATRIST ",
" PATHOLOGIST ",
" NEUROSURGEON ",
" ASSISTANT PROFESSOR ",
" OB GYN PHYSICIAN ",
" GENERAL SURGEON ",
" PHYSICAN ",
" SENIOR ASSOCIATE ",
" MUSICIAN ",
" INTERNIST ",
" CLINICAL PHARMACIST ",
" EMPLOYED PHYSICIAN ",
" NURSE ANESTHETIST ",
" PROFESSOR LAW ",
" FAMILY PRACTICE PHYSICIAN ",
" PSYCHOLOGIST ",
" PHYSICIST ",
" M D ",
" PARTNER ",
" SCIENTIST ",
" THERAPIST ",
" LPN ",
" CURATOR ",
" MINISTER ",
" NURSE PRACTITIONER ",
" VETERINARIAN ",
" CONSULTANT ",
" HIGHEST PAID ",
" MEDICAL PHYSICIST ",
" SENIOR ADVISOR ",
" FAMILY PHYSICIAN ",
" ADVANCED NURSE PRACTITIONER ",
" PUBLISHER ",
" RESEARCH SCIENTIST ",
" HOSPICE PHYSICIAN ",
" PEDIATRIC PHYSICIAN ",
" ATTENDING PHYSICIAN ",
" MEDICAL PROVIDER ",
" LAW PROFESSOR ",
" REGISTRAR ",
" ORTHOPAEDIC SURGEON ",
" RESEARCHER ",
" SENIOR RESEARCH SCIENTIST ",
" ONCOLOGIST ",
" PA ",
" PRIMARY CARE PHYSICIAN ",
" PHYSICIANS ASSISTANT ",
" STAFF PHARMACIST ",
" LIBRARIAN ",
" UROLOGIST ",
" FAMILY PRACTITIONER ",
" STAFF NURSE ",
" CLINICIAN ",
" FACULTY PHYSICIAN ",
" ADMINISTRATIVE ",
" NEUROLOGIST ",
" PHYSICIAN OB GYN ",
" PSYCHIATRIC NURSE ",
" SPEECH THERAPIST ",
" MISSIONARY ",
" GASTROENTEROLOGIST ",
" PRINCIPAL SCIENTIST ",
" TEACHER EX OFFICER SCHOOL ",
" CHARGE NURSE ",
" BASKETBALL COACH ",
" EMERGENCY PHYSICIAN ",
" RADIATION ONCOLOGIST ",
" OCCUPATIONAL THERAPIST ",
" CHIEF PHYSICIST ",
" RN SUPERVISOR ",
" APRN ",
" CHILD PSYCHIATRIST ",
" ANESTHETIST ",
" ASSISTANT FEDERAL DEFENDER ",
" LEAD TEACHER ",
" MEMBER COUNSEL ",
" OPHTHALMOLOGIST ",
" SENIOR RESEARCH FELLOW ",
" PHYSICAL THE ",
" PHYSICIAN S ASSISTANT ",
" ASSISTANT CLERK ",
" FNP ",
" ACCOUNT EXECUTIVE ",
" EDUCATOR ",
" INTERNAL MEDICINE ",
" MEDICAL STAFF ",
" PHYSICIAN CARDIOLOGY ",
" HIGHEST COMPENSATED ",
" PARAMEDIC ",
" CAPTAIN ",
" CARDIOVASCULAR SURGEON ",
" DDS ",
" NEONATOLOGIST ",
" TRAINING ",
" ASSISTANT ",
" PA C ",
" PHYSIATRIST ",
" PHYSICIAN EMPLOYEE ",
" PROFESSOR LAW ",
" FINANCIAL ",
" FAMILY PRACTICE ",
" HIGHEST PAID EMPLOYEE ",
" FORMER KEY EMPLOYEE "
)

PROFESIONAL <- PROFESIONAL %>% unique()

```

## Other Professional

```{r}
OTHER.PROF <- c(
" INSTRUCTOR ",
" PASTOR ",
" SENIOR ASSOCIATE ",
" PARTNER ",
" CURATOR ",
" MINISTER ",
" SCIENTIST ",
" THERAPIST ",
" LPN ",
" NURSE PRACTITIONER ",
" VETERINARIAN ",
" CONSULTANT ",
" HIGHEST PAID ",
" SENIOR ADVISOR ",
" PUBLISHER ",
" RESEARCH SCIENTIST ",
" REGISTRAR ",
" RESEARCHER ",
" SENIOR RESEARCH SCIENTIST ",
" LIBRARIAN ",
" ADMINISTRATIVE ",
" SPEECH THERAPIST ",
" MISSIONARY ",
" PRINCIPAL SCIENTIST ",
" TEACHER EX OFFICER SCHOOL ",
" BASKETBALL COACH ",
" ASSISTANT FEDERAL DEFENDER ",
" SENIOR RESEARCH FELLOW ",
" LEAD TEACHER ",
" ASSISTANT CLERK ",
" EDUCATOR ",
" ACCOUNT EXECUTIVE ",
" HIGHEST COMPENSATED ",
" CAPTAIN ",
" TRAINING ",
" ASSISTANT ",
" PA C ",
" HIGHEST PAID EMPLOYEE ",
" FORMER KEY EMPLOYEE ",
" FINANCIAL "
)

OTHER.PROF <- OTHER.PROF %>% unique()
```

## Medical Professional

```{r}

MED.PROF <- c(
" PHYSICIAN ",
" PSYCHIATRIST ",
" PHARMACIST ",
" DENTIST ",
" CRNA ",
" DOCTOR ",
" MD ",
" STAFF PHYSICIAN ",
" RN ",
" REGISTERED NURSE ",
" NURSE PRACTITIONER ",
" PHYSICIAN ",
" PSYCHIATRIST ",
" PHARMACIST ",
" DENTIST ",
" CRNA ",
" DOCTOR ",
" MD ",
" STAFF PHYSICIAN ",
" RN ",
" REGISTERED NURSE ",
" NURSE PRACTITIONER ",
" SURGEON ",
" PHYSICAL THERAPIST ",
" MEDICAL DOCTOR ",
" PHYSICIAN ASSISTANT ",
" CARDIOLOGIST ",
" ANESTHESIOLOGIST ",
" PEDIATRICIAN ",
" PROVIDER ",
" ER PHYSICIAN ",
" NURSE ",
" ORTHOPEDIC SURGEON ",
" HOSPITALIST ",
" SENIOR SCIENTIST ",
" OB GYN ",
" RADIOLOGIST ",
" STAFF PSYCHIATRIST ",
" PATHOLOGIST ",
" NEUROSURGEON ",
" ASSISTANT PROFESSOR ",
" OB GYN PHYSICIAN ",
" GENERAL SURGEON ",
" PHYSICAN ",
" MUSICIAN ",
" INTERNIST ",
" CLINICAL PHARMACIST ",
" EMPLOYED PHYSICIAN ",
" NURSE ANESTHETIST ",
" PROFESSOR LAW ",
" FAMILY PRACTICE PHYSICIAN ",
" PSYCHOLOGIST ",
" PHYSICIST ",
" M D ",
" MEDICAL PHYSICIST ",
" FAMILY PHYSICIAN ",
" ADVANCED NURSE PRACTITIONER ",
" HOSPICE PHYSICIAN ",
" PEDIATRIC PHYSICIAN ",
" ATTENDING PHYSICIAN ",
" MEDICAL PROVIDER ",
" ORTHOPAEDIC SURGEON ",
" ONCOLOGIST ",
" PA ",
" PRIMARY CARE PHYSICIAN ",
" PHYSICIANS ASSISTANT ",
" STAFF PHARMACIST ",
" UROLOGIST ",
" FAMILY PRACTITIONER ",
" STAFF NURSE ",
" CLINICIAN ",
" FACULTY PHYSICIAN ",
" NEUROLOGIST ",
" PHYSICIAN OB GYN ",
" PSYCHIATRIC NURSE ",
" GASTROENTEROLOGIST ",
" CHARGE NURSE ",
" EMERGENCY PHYSICIAN ",
" RADIATION ONCOLOGIST ",
" OCCUPATIONAL THERAPIST ",
" CHIEF PHYSICIST ",
" RN SUPERVISOR ",
" APRN ",
" CHILD PSYCHIATRIST ",
" ANESTHETIST ",
" OPHTHALMOLOGIST ",
" PHYSICAL THE ",
" PHYSICIAN S ASSISTANT ",
" FNP ",
" INTERNAL MEDICINE ",
" MEDICAL STAFF ",
" PHYSICIAN CARDIOLOGY ",
" PARAMEDIC ",
" CARDIOVASCULAR SURGEON ",
" DDS ",
" NEONATOLOGIST ",
" PHYSIATRIST ",
" PHYSICIAN EMPLOYEE ",
" FAMILY PRACTICE "
)
MED.PROF <- MED.PROF %>% unique()
```

## Academic Professional

```{r}
ACADEMIC.PROF <- c(
" PROFESSOR ",
" TEACHER ",
" FACULTY ",
" PROFESSOR ",
" TEACHER ",
" FACULTY ",
" LAW PROFESSOR ",
" PROFESSOR LAW "
)
ACADEMIC.PROF <- ACADEMIC.PROF %>% unique()

```

1. Seperate Problem Titles From Clean Titles
2. Create Role Variables
3. Assign Role to Clean Titles
4. Use Binary Coding on Problem Titles
5. Classify Unknown Titles
6. Code random 1000 Non Appearing Titles
7. Machine Learning Code

# Creates list all Titles
```{r}

Titles <- list (CEO = CEO, CFO = CFO, Treasurer = Treasurer, DEP.CEO = DEP.CEO, SEC = SEC, COO = COO, TRUST = TRUST, COMM = COMM, HUM.RES = HUM.RES, DEP.HEAD = DEP.HEAD, MAN = MAN, TECH = TECH, DEV = DEV, OTHER = OTHER, PROJECT = PROJECT, LEGAL = LEGAL, FACILITIES = FACILITIES, ADMIN.SUP = ADMIN.SUP, MED.MAN = MED.MAN, HEALTH.HUM = HEALTH.HUM, TRAIN = TRAIN, ACADEMIC.MAN = ACADEMIC.MAN, PROFESIONAL = PROFESIONAL, OTHER.PROF = OTHER.PROF, ACADEMIC.PROF = ACADEMIC.PROF, MED.PROF = MED.PROF)

```
# Creates List Clear Titles

```{r}
CEO.Clear <- CEO[!(CEO %in% CEO.Prob)]
CFO.Clear <- CFO[!(CFO %in% CFO.Prob)]
Treasurer.Clear <- Treasurer[!(Treasurer %in% Treasurer.Prob)]
DEP.CEO.Clear <- DEP.CEO[!(DEP.CEO %in% DEP.CEO.Prob)]
SEC.Clear <- SEC[!(SEC %in% SEC.Prob)]
COO.Clear <- COO[!(COO %in% COO.Prob)]
TRUST.Clear <- TRUST[!(TRUST %in% TRUST.Prob)]
HUM.RES.Clear <- HUM.RES[!(HUM.RES %in% HUM.RES.Prob)]
MAN.Clear <- MAN[!(MAN %in% MAN.Prob)]
DEV.Clear <- DEV[!(DEV %in% DEV.Prob)]
COMM.Clear <- COMM
TECH.Clear <- TECH

Clear.Titles <- list (CEO.Clear = CEO.Clear, CFO.Clear = CFO.Clear, Treasurer.Clear = Treasurer.Clear, DEP.CEO.Clear = DEP.CEO.Clear, SEC.Clear = SEC.Clear, COO.Clear = COO.Clear, TRUST.Clear = TRUST.Clear, HUM.RES.Clear = HUM.RES.Clear, COMM.Clear = COMM.Clear, MAN.Clear = MAN.Clear, TECH.Clear = TECH.Clear, DEV.Clear = DEV.Clear)

```

# Creates List Problem Titles

```{r}
Problem.Titles <- list( CEO.Board = CEO.Board, CEO.Prob = CEO.Prob, CFO.Prob = CFO.Prob, Treasurer.Prob = Treasurer.Prob, DEP.CEO.Prob = DEP.CEO.Prob, SEC.Prob = SEC.Prob, COO.Prob = COO.Prob, TRUST.Prob = TRUST.Prob, HUM.RES.Prob = HUM.RES.Prob, MAN.Prob = MAN.Prob, DEV.Prob = DEV.Prob, CEO.SCHOOL = CEO.SCHOOL, CEO.Prob.Other = CEO.Prob.Other, TRUST.Prob.BOARD = TRUST.Prob.BOARD, TRUST.Prob.DEP.CEO = TRUST.Prob.DEP.CEO, TRUST.Prob.MAN = TRUST.Prob.MAN, TRUST.Prob.OTHER = TRUST.Prob.OTHER, SCHOOL.HEAD = SCHOOL.HEAD )
```


# CreatesSaves Lists all titles

```{r}
All.Titles <- c(Titles, Clear.Titles, Problem.Titles)

save( All.Titles, file = "Data/title-list.Rdata")
```
